---
title: "Diff. exp comparison"
author: "Andrew Chen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: 'united'
    toc: true
    toc_depth: 1
    toc_float: true
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE}
library(tidyverse)
PATH <- file.path(Sys.getenv("MLAB"), "projects/brcameta/brca_atlas")
source(file.path(PATH, "../sig_recon/scripts/util.R"))
```

# Loading Data
```{r}
#imm
imm_04_wilcox_markers <- readRDS(file.path(PATH, "results/clustering/imm_04_wilcox_markers.rds"))
imm_04_wilcox_center_markers <- readRDS(file.path(PATH, "results/clustering/imm_04_wilcox_center_markers.rds"))
imm_04_wilcox_scale_center_markers <- readRDS(file.path(PATH, "results/clustering/imm_04_wilcox_scale_center_markers.rds"))
myeloid_04_mast_markers <- readRDS(file.path(PATH, "results/clustering/myeloid_04_mast_markers.rds"))
lymphoid_04_mast_markers <- readRDS(file.path(PATH, "results/clustering/lymphoid_04_mast_markers.rds"))
#strom
strom_04_wilcox_markers <- readRDS(file.path(PATH, "results/clustering/strom_04_wilcox_markers.rds"))
strom_04_wilcox_center_markers <- readRDS(file.path(PATH, "results/clustering/strom_04_wilcox_center_markers.rds"))
strom_04_wilcox_scale_center_markers <- readRDS(file.path(PATH, "results/clustering/strom_04_wilcox_scale_center_markers.rds"))
strom_04_mast_markers <- readRDS(file.path(PATH, "results/clustering/strom_04_mast_markers.rds"))
#epi
epi_02_wilcox_markers <- readRDS(file.path(PATH, "results/clustering/epi_02_wilcox_markers.rds"))
epi_02_wilcox_center_markers <- readRDS(file.path(PATH, "results/clustering/epi_02_wilcox_center_markers.rds"))
epi_02_wilcox_scale_center_markers <- readRDS(file.path(PATH, "results/clustering/epi_02_wilcox_scale_center_markers.rds"))
epi_02_mast_markers <- readRDS(file.path(PATH, "results/clustering/epi_02_mast_markers.rds"))
```

# Background

This is slow.
```
Seurat::FindAllMarkers(..., test.use="MAST", latent.vars="batch")
```

This is faster.
```
Seurat::FindAllMarkers(..., test.use="wilcox")
```

Motivating questions:

1) How different are they?

2) What about gene centering? 
`ScaleData(do.center = TRUE, do.scale = FALSE, features = rownames(seurat_obj))`
Or 
`ScaleData(do.center = TRUE, do.scale = TRUE, features = rownames(seurat_obj))`

```{r}
imm_center_markers <- imm_04_wilcox_center_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(imm_center_markers, function(x) unique(x$cluster)) %>% unlist
imm_center_markers <- lapply(imm_center_markers, function(x) x %>% dplyr::pull(gene))
names(imm_center_markers) <- cluster_names

imm_center_markers_50 <- lapply(imm_center_markers, function(x) x[1:50])

imm_scale_center_markers <- imm_04_wilcox_scale_center_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(imm_scale_center_markers, function(x) unique(x$cluster)) %>% unlist
imm_scale_center_markers <- lapply(imm_scale_center_markers, function(x) x %>% dplyr::pull(gene))
names(imm_scale_center_markers) <- cluster_names

imm_scale_center_markers_50 <- lapply(imm_scale_center_markers, function(x) x[1:50])

imm_markers <- imm_04_wilcox_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(imm_markers, function(x) unique(x$cluster)) %>% unlist
imm_markers <- lapply(imm_markers, function(x) x %>% dplyr::pull(gene))
names(imm_markers) <- cluster_names

imm_markers_50 <- lapply(imm_markers, function(x) x[1:50])

myeloid_markers <- myeloid_04_mast_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(myeloid_markers, function(x) unique(x$cluster)) %>% unlist
myeloid_markers <- lapply(myeloid_markers, function(x) x %>% dplyr::pull(gene))
names(myeloid_markers) <- cluster_names

myeloid_markers_50 <- lapply(myeloid_markers, function(x) x[1:50])

lymphoid_markers <- lymphoid_04_mast_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(lymphoid_markers, function(x) unique(x$cluster)) %>% unlist
lymphoid_markers <- lapply(lymphoid_markers, function(x) x %>% dplyr::pull(gene))
names(lymphoid_markers) <- cluster_names

lymphoid_markers_50 <- lapply(lymphoid_markers, function(x) x[1:50])
```

```{r}
strom_center_markers <- strom_04_wilcox_center_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(strom_center_markers, function(x) unique(x$cluster)) %>% unlist
strom_center_markers <- lapply(strom_center_markers, function(x) x %>% dplyr::pull(gene))
names(strom_center_markers) <- cluster_names

strom_center_markers_50 <- lapply(strom_center_markers, function(x) x[1:50])

strom_scale_center_markers <- strom_04_wilcox_scale_center_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(strom_scale_center_markers, function(x) unique(x$cluster)) %>% unlist
strom_scale_center_markers <- lapply(strom_scale_center_markers, function(x) x %>% dplyr::pull(gene))
names(strom_scale_center_markers) <- cluster_names

strom_scale_center_markers_50 <- lapply(strom_scale_center_markers, function(x) x[1:50])

strom_markers <- strom_04_wilcox_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(strom_markers, function(x) unique(x$cluster)) %>% unlist
strom_markers <- lapply(strom_markers, function(x) x %>% dplyr::pull(gene))
names(strom_markers) <- cluster_names

strom_markers_50 <- lapply(strom_markers, function(x) x[1:50])

strom_mast_markers <- strom_04_mast_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(strom_mast_markers, function(x) unique(x$cluster)) %>% unlist
strom_mast_markers <- lapply(strom_mast_markers, function(x) x %>% dplyr::pull(gene))
names(strom_mast_markers) <- cluster_names

strom_mast_markers_50 <- lapply(strom_mast_markers, function(x) x[1:50])
```

```{r}
epi_center_markers <- epi_02_wilcox_center_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(epi_center_markers, function(x) unique(x$cluster)) %>% unlist
epi_center_markers <- lapply(epi_center_markers, function(x) x %>% dplyr::pull(gene))
names(epi_center_markers) <- cluster_names

epi_center_markers_50 <- lapply(epi_center_markers, function(x) x[1:50])

epi_scale_center_markers <- epi_02_wilcox_scale_center_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(epi_scale_center_markers, function(x) unique(x$cluster)) %>% unlist
epi_scale_center_markers <- lapply(epi_scale_center_markers, function(x) x %>% dplyr::pull(gene))
names(epi_scale_center_markers) <- cluster_names

epi_scale_center_markers_50 <- lapply(epi_scale_center_markers, function(x) x[1:50])

epi_markers <- epi_02_wilcox_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(epi_markers, function(x) unique(x$cluster)) %>% unlist
epi_markers <- lapply(epi_markers, function(x) x %>% dplyr::pull(gene))
names(epi_markers) <- cluster_names

epi_markers_50 <- lapply(epi_markers, function(x) x[1:50])

epi_mast_markers <- epi_02_mast_markers %>% 
  dplyr::group_by(cluster) %>%
  dplyr::arrange(p_val_adj, desc(avg_log2FC)) %>% 
  dplyr::group_split()
cluster_names <- lapply(epi_mast_markers, function(x) unique(x$cluster)) %>% unlist
epi_mast_markers <- lapply(epi_mast_markers, function(x) x %>% dplyr::pull(gene))
names(epi_mast_markers) <- cluster_names

epi_mast_markers_50 <- lapply(epi_mast_markers, function(x) x[1:50])
```

# Epi {.tabset}

## Epi Wilcox (gc) v Wilcox
```{r}
vjaccard(epi_markers_50, epi_center_markers_50) %>% 
  data.frame(cluster = names(epi_center_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

## Epi Wilcox (gc + sc) v Wilcox
```{r}
vjaccard(epi_markers_50, epi_scale_center_markers_50) %>% 
  data.frame(cluster = names(epi_scale_center_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```


## Epi Mast v Wilcox
```{r}
vjaccard(epi_mast_markers_50, epi_scale_center_markers_50) %>% 
  data.frame(cluster = names(epi_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

# Stromal {.tabset}

## Strom Wilcox (gc) v Wilcox
```{r}
vjaccard(strom_markers_50, strom_center_markers_50) %>% 
  data.frame(cluster = names(strom_center_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

## Strom Wilcox (gc + sc) v Wilcox
```{r}
vjaccard(strom_markers_50, strom_scale_center_markers_50) %>% 
  data.frame(cluster = names(strom_scale_center_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

## Strom Mast v Wilcox
```{r}
vjaccard(strom_mast_markers_50, strom_scale_center_markers_50) %>% 
  data.frame(cluster = names(strom_center_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

# Immune {.tabset}

## Imm Wilcox (gc) vs Wilcox
```{r}
vjaccard(imm_center_markers_50, imm_markers_50) %>% 
  data.frame(cluster = names(imm_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

## Imm Wilcox (gc + sc) vs Wilcox
```{r}
vjaccard(imm_scale_center_markers_50, imm_markers_50) %>% 
  data.frame(cluster = names(imm_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

## Imm Wilcox vs Mast (Myeloid Only)
```{r}
vjaccard(imm_scale_center_markers_50[names(myeloid_markers_50)], myeloid_markers_50) %>% 
  data.frame(cluster = names(myeloid_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```

## Imm Wilcox vs Mast (Lymphoid Only)
```{r}
vjaccard(imm_scale_center_markers_50[names(lymphoid_markers_50)], lymphoid_markers_50) %>% 
  data.frame(cluster = names(lymphoid_markers_50), jacc = .) %>%
  ggplot(aes(x = cluster, y = jacc, fill = cluster)) +
  geom_bar(stat = "identity") +
  labs(title = "jaccard similarity of top 50 Diff Exp genes")
```