---
title: "Imm Clusters"
author: "Andrew Chen"
date: "`r format(Sys.Date(),'%e, %B, %Y')`"
output:
  html_document:
    theme: 'united'
    toc: true
    toc_depth: 1
    toc_float: true
    df_print: paged 
    code_folding: hide
    fig_width: 15 
    fig_height: 10 
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(Seurat)
library(scCustomize)
library(ggrepel)
PATH <- file.path(Sys.getenv("MLAB"), "projects/brcameta/brca_atlas/")
source("util.R")
options(ggrepel.max.overlaps = Inf)

```

# Loading Data
```{r}
imm_rpca <- readRDS(file.path(PATH, "data/sc/imm_rpca_subset.rds"))
```

```{r}
boroni_sigs <- readRDS(file.path(PATH, "data/signatures/immune/boroni_2024/pan_cancer_myeloid_sigs.rds"))
boroni_sigs <- lapply(boroni_sigs, function(x) x[x %in% rownames(imm_rpca)])
boroni_sigs <- boroni_sigs[as.numeric(lapply(boroni_sigs, length)) > 0]

immune_celltypes <- readRDS(file.path(PATH, "data/signatures/immune/combined_celltypes.rds"))
immune_celltypes <- lapply(immune_celltypes, function(x) x[x %in% rownames(imm_rpca)])
immune_pathways <- readRDS(file.path(PATH, "data/signatures/immune/immune_pathways.rds"))
immune_pathways <- lapply(immune_pathways, function(x) x[x %in% rownames(imm_rpca)])
```

## Annotations {.tabset}

## All
```{r}
imm_rpca$celltypist_imm_only <- with(imm_rpca@meta.data, 
                                     case_when(celltypist_broad == "Immune" ~ celltypist_pred,
                                               .default = celltypist_broad))
imm_rpca$singler_pred <- str_replace(imm_rpca$singler_pred, ", alpha-beta T cell", "")
imm_rpca$singler_pred <- str_replace(imm_rpca$singler_pred, ", alpha-beta memory T cell", " memory")
imm_rpca$singler_pred <- str_replace(imm_rpca$singler_pred, " positive memory", "positive memory")
imm_rpca$singler_pred <- str_replace(imm_rpca$singler_pred, "conventional dendritic cell", "cDC")
imm_rpca$singler_pred <- str_replace(imm_rpca$singler_pred, "plasmacytoid dendritic cell", "cDC")
imm_rpca$singler_pred <- str_replace(imm_rpca$singler_pred, "cell", "")
imm_rpca$singler_imm_only <- with(imm_rpca@meta.data, 
                                  case_when(singleR_broad == "Immune" ~ singler_pred,
                                            .default = singleR_broad))
imm_rpca$author_imm_only <- with(imm_rpca@meta.data, 
                                 case_when(author_broad == "Immune" ~ celltype_new,
                                           .default = author_broad))
Idents(imm_rpca) <- imm_rpca$RNA_snn_res.0.4

p1 <- DimPlot_scCustom(imm_rpca,
                       reduction = "umap.rpca",
                       group.by = "RNA_snn_res.0.4",
                       label = TRUE,
                       label.size = 3,
                       raster = FALSE,
                       repel = TRUE) + labs(title = "Clustering (0.4)", x = "UMAP 1", y = "UMAP 2")
p2 <- DimPlot_scCustom(seurat_object = imm_rpca,
                       group.by = "celltypist_imm_only",
                       reduction = "umap.rpca",
                       label = TRUE,
                       label.size = 1.5,
                       label.box = TRUE,
                       repel = TRUE,
                       raster = FALSE) + 
  labs(title = "Celltypist", x = "UMAP 1", y = "UMAP 2") +
  theme(legend.position = "none")
p3 <- DimPlot_scCustom(seurat_object = imm_rpca,
                       group.by = "singler_imm_only",
                       reduction = "umap.rpca",
                       label = TRUE,
                       label.size = 1.5, 
                       label.box = TRUE,
                       repel = TRUE,
                       raster = FALSE) + 
  labs(title = "SingleR", x = "UMAP 1", y = "UMAP 2") +
  theme(legend.position = "none")
p4 <- DimPlot_scCustom(imm_rpca,
                       reduction = "umap.rpca",
                       group.by = "author_imm_only",
                       label = TRUE,
                       label.size = 1.5,
                       label.box = TRUE,
                       repel = TRUE, 
                       raster = FALSE) + 
  labs(title = "Author", x = "UMAP 1", y = "UMAP 2") +
  theme(legend.position = "none")
combined <- cowplot::plot_grid(p1, p2, p3, p4, ncol = 2, nrow = 2)
ggsave(plot = combined, filename = file.path(PATH, "results/umaps/imm_rpca_annot_04.png"), height = 8, width = 9)
combined
```


# T + NK {.tabset}
```{r}
t_nk <- c("CD3E", "CD4", "CD8A", "NKG7")
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = t_nk)
```

```{r}
names(boroni_sigs[27:37])
```

## NK_rest
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`NK_rest`)
```

## NK_cyto
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`NK_cyto`)
```

## NKT
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`NKT`)
```

## CD4_naive
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`TCD4_naive`)
```

## CD8_naive
```{r}
cd8_naive <- unique(c(boroni_sigs$`TCD8_naive`, immune_pathways$CD8_naive))
```

```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = cd8_naive[1:4])
```

## CD4_em
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`TCD4_em`)
```

## CD8_em
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`TCD8_em`)
```

## CD4_ex
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`TCD4_ex`)
```

## CD8_ex
```{r}
cd8_ex <- unique(c(boroni_sigs$TCD8_ex, immune_pathways$CD8_Tex))
```

```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = cd8_ex[1:10])
```

## CD4_reg
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`TCD4_reg`)
```

## CD4 Tfh
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = immune_pathways$CD4_Tfh[1:4])
```

## CD8 Predysfunctional
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = immune_pathways$CD8_predysfunc[1:4])
```

## CD8 Dysfunctional
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = immune_pathways$CD8_dysfunctional[1:4])
```

## CD8 Cytotoxic
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = immune_pathways$CD8_cytotoxic[1:4])
```

## CD8 TRM
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = immune_pathways$CD8_TRM[1:4])
```

## CD8/CD4 T sr
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = immune_pathways$CD4_CD8_Tstr[1:4])
```

# Myeloid {.tabset}
```{r}
phagocytes <- c("LYZ", "AIF1", "CD68")
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = phagocytes)
```

```{r}
names(boroni_sigs)[str_detect(names(boroni_sigs), pattern = "Mono|Mac|RTM|cDC|Neutrophil")]
```

## Monocytes {.tabset}

### Mono_FCGR3A
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mono_FCGR3A`)
```

### Mono_CD14_FOS-
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mono_CD14_FOS-`)
```

### Mono_CD14_FOS+
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mono_CD14_FOS+`)
```

### Mono_IL1B
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mono_IL1B`)
```

### MonoInter_CXCL10
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`MonoInter_CXCL10`)
```

### MonoInter_CLEC10A
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`MonoInter_CLEC10A`)
```

## Macrophages {.tabset}

### Mac_Alv_like
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_Alv_like`)
```

### Mac_Angio
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_Angio`)
```

### Mac_Hypo
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_Hypo`)
```

### Mac_ES
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_ES`)
```

### Mac_IFN
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_IFN`)
```

### Mac_LA
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_LA`)
```

### Mac_AgPres
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`Mac_AgPres`)
```

### RTM_IFN
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`RTM_IFN`)
```

### RTM_like_MT
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`RTM_like_MT`)
```

## Mast Cells

```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = c("TPSAB1", "CMA1"))
```

# Neutrophils 
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = c(boroni_sigs$`Neutrophil_TAGLN2`, boroni_sigs$`Neutrophil_MMP9`))
```

# B cells
```{r}
b_cells <- c("MS4A1", "MZB1")
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = b_cells)
```

# Dendritic {.tabset}
```{r}
dendritic <- c("LILRA4", "IRF7")
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = dendritic)
```

## cDC1_CLEC9A
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC1_CLEC9A`)
```

## cDC2_AREG
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC2_AREG`)
```

## cDC2_FCER1A
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC2_FCER1A`)
```

## cDC3_CD14
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC3_CD14`)
```

## cDC4_FCGR3A
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC4_FCGR3A`)
```

## cDC_CXCL8
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC_CXCL8`)
```

## cDC2_CD207
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC2_CD207`)
```

## cDC_LAMP3
```{r}
Plot_Density_Custom(imm_rpca,
                    reduction = "umap.rpca",
                    features = boroni_sigs$`cDC_LAMP3`)
```
