---
title: "Strom Clusters"
author: "Andrew Chen"
date: "`r format(Sys.Date(),'%e, %B, %Y')`"
output:
  html_document:
    theme: 'united'
    toc: true
    toc_depth: 1
    toc_float: true
    df_print: paged 
    code_folding: hide
    fig_width: 15 
    fig_height: 10 
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
library(Seurat)
library(scCustomize)
library(ggrepel)
PATH <- file.path(Sys.getenv("MLAB"), "projects/brcameta/brca_atlas/")
source("util.R")
options(ggrepel.max.overlaps = Inf)

```

# Loading Data
```{r}
strom_rpca <- readRDS(file.path(PATH, "data/sc/strom_rpca_subset.rds"))
```

# Annotations
```{r}
strom_rpca$celltypist_strom_only <- with(strom_rpca@meta.data, 
                                     case_when(celltypist_broad == "Stromal" ~ celltypist_pred,
                                               .default = celltypist_broad))
strom_rpca$singler_strom_only <- with(strom_rpca@meta.data, 
                                     case_when(singleR_broad == "Stromal" ~ singler_pred,
                                               .default = singleR_broad))
strom_rpca$author_strom_only <- with(strom_rpca@meta.data, 
                                     case_when(author_broad == "Stromal" ~ celltype_new,
                                               .default = author_broad))
Idents(strom_rpca) <- strom_rpca$RNA_snn_res.0.4
p1 <- DimPlot_scCustom(strom_rpca,
                       reduction = "umap.rpca",
                       group.by = "RNA_snn_res.0.4",
                       label = TRUE,
                       label.size = 3,
                       repel = TRUE, 
                       raster = FALSE) + labs(title = "Clustering (0.4)", x = "UMAP 1", y = "UMAP 2")
p2 <- DimPlot_scCustom(strom_rpca,
                       reduction = "umap.rpca",
                       group.by = "celltypist_strom_only",
                       label = TRUE,
                       label.size = 1.5,
                       label.box = TRUE,
                       repel = TRUE, 
                       raster = FALSE) + 
  labs(title = "Celltypist", x = "UMAP 1", y = "UMAP 2") +
  theme(legend.position = "none")
p3 <- DimPlot_scCustom(strom_rpca,
                       reduction = "umap.rpca",
                       group.by = "singler_strom_only",
                       label = TRUE,
                       label.size = 1.5,
                       label.box = TRUE,
                       repel = TRUE, 
                       raster = FALSE) + 
  labs(title = "SingleR", x = "UMAP 1", y = "UMAP 2") +
  theme(legend.position = "none")
p4 <- DimPlot_scCustom(strom_rpca,
                       reduction = "umap.rpca",
                       group.by = "author_strom_only",
                       label = TRUE,
                       label.size = 1.5,
                       label.box = TRUE,
                       repel = TRUE, 
                       raster = FALSE) + 
  labs(title = "Author", x = "UMAP 1", y = "UMAP 2") +
  theme(legend.position = "none")
combined <- cowplot::plot_grid(p1, p2, p3, p4, ncol = 2, nrow = 2)
ggsave(plot = combined, filename = file.path(PATH, "results/umaps/stromal_rpca_annot_04.png"), height = 8, width = 9)
combined
```

# Loading markers
```{r}
endothelial <- c("PLVAP", "CLDN5")
mural <- c("RGS5", "ACTA2", "PDGFRB")
fibroblasts <- c("COL1A1", "DCN", "LUM")
mesothelial <- c("KRT19", "MSLN", "CALB2")
prolif_stromal <- c("STMN1", "TOP2A", "MKI67")
glial <- c("GPM6B", "CDH19")

pan_cancer_stromal_sigs <- readRDS(file.path(PATH, "data/signatures/stromal/ye_2024/pan_cancer_stromal_sigs.rds"))
pan_cancer_stromal_sigs <- lapply(pan_cancer_stromal_sigs, function(x) x[x %in% rownames(strom_rpca)])

strom_sigs <- readRDS(file.path(PATH, "/data/signatures/stromal/wu_embo_2020/strom_sigs.rds"))
strom_sigs <- lapply(strom_sigs, function(x) x[x %in% rownames(strom_rpca)])
```

# Endothelial {.tabset}
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = endothelial)
```

Endothelial subpopulations
```{r}
names(pan_cancer_stromal_sigs)[str_detect(names(pan_cancer_stromal_sigs), "ECs")]
```

```{r}
ec_sub_sigs <- pan_cancer_stromal_sigs[str_detect(names(pan_cancer_stromal_sigs), "ECs")]
ec_sub_sigs_top4 <- lapply(ec_sub_sigs, function(x) x[1:4])
```

## Aerocytes ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Aerocytes ECs`)
```

## Arterial ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Arterial ECs`)
```

## CD14+ circECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`CD14+ circECs`)
```

## Capillaries ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Capillaries ECs`)
```

## FOS+ Capillaries ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`FOS+ Capillaries ECs`)
```

## ISG15+ ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`ISG15+ ECs`)
```

## Immature ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Immature ECs`)
```

## Lymphatic ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Lymphatics ECs`)
```

## Venous ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Venous ECs`)
```

## Venous IL6+ ECs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = ec_sub_sigs_top4$`Venous IL6+ ECs`)
```

# Mural Cells {.tabset}
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural)
```
Mural subpopulations
```{r}
names(pan_cancer_stromal_sigs)[str_detect(names(pan_cancer_stromal_sigs), "SMCs|PCs")]
```

```{r}
mural_sub_sigs <- pan_cancer_stromal_sigs[str_detect(names(pan_cancer_stromal_sigs), "SMCs|PCs")]
mural_sub_sigs_top4 <- lapply(mural_sub_sigs, function(x) x[1:4])
```

## iPVL
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = strom_sigs$ipvl[1:4])
```

## dPVL
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = strom_sigs$dpvl[1:4])
```

## ATF3+ PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`ATF3+ PCs`)
```

## ATF3+ SMCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`ATF3+ SMCs`)
```

## CCL19+ PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`CCL19+ PCs`)
```

## ECM PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`ECM PCs`)
```


## FABP4+ PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`FABP4+ PCs`)
```

## Fibrogenic PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`Fibrogenic PCs`)
```

## HTRA3+ PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`HTRA3+ PCs`)
```

## ISG15+ PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`ISG15+ PCs`)
```

## RERGL high SMCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`RERGL high SMCs`)
```

## RERGL low SMCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`RERGL low SMCs`)
```


## SERPINE1+ PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`SERPINE1+ PCs`)
```

## Vascular PCs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mural_sub_sigs_top4$`Vascular PCs`)
```


# Fibroblast Cells {.tabset}
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fibroblasts)
```

Fibroblast subpopulations
```{r}
names(pan_cancer_stromal_sigs)[str_detect(names(pan_cancer_stromal_sigs), "Fib|CAFs")]
```

```{r}
fib_sub_sigs <- pan_cancer_stromal_sigs[str_detect(names(pan_cancer_stromal_sigs), "Fib|CAFs")]
fib_sub_sigs_top4 <- lapply(fib_sub_sigs, function(x) x[1:4])
```

## myCAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = strom_sigs$mycafs[1:4])
```

## iCAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = strom_sigs$icafs[1:4])
```

## ADAMDEC1+ TrsFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`ADAMDEC1+ TrsFib`)
```

## ATF3+ PanFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`ATF3+ PanFib`)
```

## CA12+ CAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`CA12+ CAFs`)
```

## CCL19+ Fib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`CCL19+ Fib`)
```

## COL11A1+ CAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`COL11A1+ CAFs`)
```

## DPT+ PanFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`DPT+ PanFib`)
```


## IL6+ iCAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`IL6+ iCAFs`)
```

## ISG15+ CAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`ISG15+ CAFs`)
```

## LAMP5+ CAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`LAMP5+ CAFs`)
```

## MYH11+ myoFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`MYH11+ myoFib`)
```

## NPNT+ TrsFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`NPNT+ TrsFib`)
```

## PI16+ PanFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`PI16+ PanFib`)
```


## SFRP4+ CAFs
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`SFRP4+ CAFs`)
```

## SOX6+ TrsFib
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = fib_sub_sigs_top4$`SOX6+ TrsFib`)
```

# Mesothelial Cells 
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = mesothelial)
```


# Prolif. Stromal Cells 
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = prolif_stromal)
```


# Glial Cells 
```{r}
Plot_Density_Custom(strom_rpca, reduction = "umap.rpca", features = glial)
```