---
title: "Main Figures"
author: "Andrew Chen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: 'united'
    toc: true
    toc_depth: 1
    toc_float: true
    df_print: paged
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(Seurat)
library(cowplot)
library(emmeans)
library(scCustomize)
library(ggradar)
library(ggsankey)
library(sccomp)
library(SummarizedExperiment)
library(brcasurv)
# library(K2Taxonomer)
# library(dendextend)
# library(ComplexHeatmap)
# library(fastDummies)
# library(circlize)
# library(Biobase)
# library(visNetwork)

PATH <- file.path(Sys.getenv("MLAB"), "projects/brcameta/brca_atlas")
# source(file.path(PATH,"../personal/andrewdr/k2_dge_script.R"))
source(file.path(PATH, "../personal/andrewdr/grant_figures/dot_plot.R"))
source(file.path(PATH, "scripts/util.R"))
```

# Figure 1

```{r}
combined_seurat_rpca <- readRDS(file.path(PATH, "data/sc/combined_seurat_rpca.rds"))
```

## By batch
```{r}
DimPlot_scCustom(combined_seurat_rpca,
                 reduction = "umap.rpca",
                 group.by = "batch",
                 raster = FALSE) + labs(title = "Integrated Core Atlas", x = "UMAP 1", y = "UMAP 2")
ggsave(filename = file.path(PATH, "results/final_figures/integrated_core_atlas_batches.png"), width = 6, height = 6)
```

## Metadata Plots

### Patient
```{r}
varibow_pal <- DiscretePalette_scCustomize(num_colors = 145, palette = "varibow")
batch_summary <- combined_seurat_rpca@meta.data %>%
  group_by(batch) %>%
  summarize(
    total_cells = n(),
    unique_donors = n_distinct(donor)
  ) %>% arrange(desc(total_cells))

combined_seurat_rpca@meta.data %>% 
  dplyr::count(batch, donor) %>% 
  dplyr::group_by(batch) %>% 
  dplyr::mutate(unique_donors = n_distinct(donor),
                total_cells = sum(n)) %>% 
  dplyr::ungroup() %>%
  ggplot(aes(x = reorder(batch, total_cells, decreasing = TRUE), fill = donor, y = n)) + 
  geom_col(position = "stack", colour = "black") +
  geom_text(
    aes(y = total_cells, label = unique_donors),
    vjust = -0.5,
    size = 5
  ) + 
  scale_fill_manual(values = varibow_pal) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1))) +
  theme_minimal() + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1)) + 
  labs(x = NULL, y = "Cells") 

ggsave(filename = file.path(PATH, "results/final_figures/cells_patient.png"), height = 5, width = 6)
```

### Celltypist 
```{r}
varibow_pal <- DiscretePalette_scCustomize(num_colors = 20, palette = "varibow")
combined_seurat_rpca$celltypist_short <- celltypist_short(combined_seurat_rpca$celltypist_pred)
combined_seurat_rpca@meta.data %>% 
  dplyr::count(batch, celltypist_short) %>% 
  ggplot(aes(x = reorder(batch, n, sum, decreasing = TRUE), fill = celltypist_short, y = n)) + 
  geom_col(position = "fill", colour = "black") +
  scale_fill_manual(values = varibow_pal) +
  theme_minimal() + 
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1)) + 
  labs(x = NULL, y = "Cells", fill = "Cell Type")

ggsave(filename = file.path(PATH, "results/final_figures/batch_celltypes.png"), width = 10, height = 8)
```

### Subtype + Grade
```{r}
ditto_pal <- DiscretePalette_scCustomize(num_colors = 4, palette="ditto_seq")
combined_seurat_rpca@meta.data %>% 
  dplyr::group_by(subtype_new, grade) %>% 
  dplyr::summarize(count = n_distinct(donor)) %>% 
  ggplot(aes(x = reorder(subtype_new, -count, sum), fill = as.factor(grade), y = count)) + 
  geom_col(position = "stack", colour = "black") +
  scale_fill_manual(values = ditto_pal) +
  theme_minimal() + 
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1)) + 
  labs(x = NULL, y = "# Samples", fill = "Grade")

ggsave(filename = file.path(PATH, "results/final_figures/metadata_subtype_grade.png"), width = 6, height = 6)
```

### Subtype Only
```{r}
combined_seurat_rpca@meta.data %>% 
  dplyr::group_by(subtype_new) %>%
  dplyr::summarise(count = n_distinct(donor)) %>%
  
  ggplot(aes(x = reorder(subtype_new, -count), y = count, fill = subtype_new)) +
  scale_fill_manual(values = ditto_pal) +
  geom_bar(stat="identity") + 
  labs(x = "Subtype", y = "# Samples") +
  theme_minimal() + 
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
        legend.position = "none")

ggsave(filename = file.path(PATH, "results/final_figures/metadata_subtype.png"), width = 6, height = 6)
```


### Age
```{r}
combined_seurat_rpca@meta.data %>%
  ggplot(aes(x = age, y = ..density..)) +
  geom_histogram(bins=20, color = "black", fill = "salmon") +
  labs(x = "Age", y = "Density") +
  theme_minimal() + 
  theme(text = element_text(size = 20),
        legend.position = "none")
ggsave(file.path(PATH, "results/final_figures/metadata_age.png"), height = 6, width = 6)
```


# Figure 2 

## Metrics
```{r}
bm_comb <- read.csv(file.path(PATH,  "results/benchmark/combined/celltype/bm_combined.csv"))
bm_comb
```

```{r}
bm_comb <- bm_comb %>% dplyr::filter(Embedding %in% c("Unintegrated", 
                                                      "X_scANVI_30_ct", 
                                                      "X_scVI_30", 
                                                      "X_seurat_harmony", 
                                                      "X_seurat_rpca", 
                                                      "X_seurat_mnn"))
bm_comb <- bm_comb %>% rename("Silhouette" = "Silhouette.batch",
                              "PCR" = "PCR.comparison")

bm_comb$Embedding <- c("Unintegrated", 
                       "scANVI", 
                       "scVI",
                       "harmony", 
                       "rpca", 
                       "mnn")
ditto_pal <- DiscretePalette_scCustomize(num_colors = 6, palette="ditto_seq")
ditto_pal[3] <- "#FF00FF"
bm_plot <- bm_comb %>% 
  dplyr::select(c("Embedding", "Silhouette", "iLISI", "KBET")) %>%
  mutate_at(vars(-Embedding), as.numeric) %>%
  mutate_at(vars(-Embedding), scales::rescale) %>%
  dplyr::rename("group"= "Embedding") %>%
  ggradar(values.radar = c("0", "0.5", "1.0"),
          grid.label.size = 5, 
          group.line.width = 0.5, 
          group.point.size = 2,
          plot.legend=TRUE,
          gridline.mid.colour = "grey",
          group.colours = ditto_pal,
          label.gridline.max = TRUE)
bm_plot
ggsave(file.path(PATH, "results/final_figures/integration_benchmarking.png"), height = 6, width = 6)
```

## Broad Clusters
```{r}
DimPlot_scCustom(combined_seurat_rpca,
                 reduction = "umap.rpca",
                 group.by = "cluster_broad",
                 colors_use = c("#5A5156FF", "#F6222EFF", "#FF00FF"),
                 raster = FALSE) + labs(title = "Broad Clusters", x = "UMAP 1", y = "UMAP 2")
ggsave(filename = file.path(PATH, "results/final_figures/all_clustering_broad_final.png"), width = 5, height = 4)
```

## Broad Cell type by Patient
```{r}
polychrom_pal <- DiscretePalette_scCustomize(num_colors = 10, palette = "polychrome")
combined_seurat_rpca@meta.data %>% 
  dplyr::count(cluster_broad, batch) %>% 
  ggplot(aes(x = reorder(cluster_broad, n, sum, decreasing = TRUE), fill = batch, y = n)) + 
  geom_col(position = "stack", colour = "black") +
  scale_fill_manual(values = polychrom_pal) +
  theme_minimal() + 
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1)) + 
  labs(x = NULL, y = "Cells")
ggsave(filename = file.path(PATH, "results/final_figures/cells_broad_compartment.png"), width = 8, height = 6)
```

## Dot Plot
```{r}
strom_genes <- c("COL1A1", "COL1A2", "ENG")
epi_genes <- c("EPCAM", "KRT8","KRT18")
imm_genes <- c("PTPRC", "CD3D", "CD3E", "CD68")
all_markers <- c(strom_genes, imm_genes, epi_genes)
DotPlot_scCustom(seurat_object = combined_seurat_rpca,
                 features = all_markers, group.by="cluster_broad",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE) + guides(color = guide_colorbar(title = "Average Scaled \nExpression"))

ggsave(filename = file.path(PATH, "results/dotplots/all_broad_markers.png"), height = 4, width = 6)
```

## Sankey
```{r}
df <- combined_seurat_rpca@meta.data %>% 
  dplyr::mutate(All = "All") %>%
  dplyr::select(All, author_broad, cluster_broad) %>% 
  dplyr::rename("Author" = author_broad, "Atlas" = cluster_broad) %>% 
  ggsankey::make_long("All", "Author", "Atlas")

df <- df %>% 
  dplyr::mutate(node = factor(node, levels = c("All", "Unassigned", "Stromal", "Immune", "Epithelial")),
                next_node = factor(next_node, levels = c("Unassigned", "Stromal", "Immune", "Epithelial")))
```


```{r}
ggplot(df, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = node, label = node)) +
  geom_sankey(flow.alpha = .6,
              node.color = "gray30",
              smooth = 4) +
  geom_sankey_label(size = 3, color = "white", fill = "gray40") +
  scale_fill_viridis_d(drop = FALSE) +
  theme_sankey(base_size = 18) +
  labs(x = NULL) +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5)) 
ggsave(file.path(PATH, "results/final_figures/atlas_annot.png"), width = 6, height = 6)
```

```{r}
# Mislabeled cells - 9172 cells across 5 datasets
mislabeled_cells <- combined_seurat_rpca@meta.data %>% 
  dplyr::filter(author_broad != "Unassigned") %>% 
  dplyr::filter(author_broad != cluster_broad) %>% rownames
mislabeled_subset <- combined_seurat_rpca[,mislabeled_cells]
```


```{r}
strom_genes <- c("COL1A1", "COL1A2", "ENG")
epi_genes <- c("EPCAM", "KRT8","KRT18")
imm_genes <- c("PTPRC", "CD68", "CD3D", "CD3E")
all_markers <- c(strom_genes, imm_genes, epi_genes)
DotPlot_scCustom(seurat_object = mislabeled_subset,
                 features = all_markers, group.by="cluster_broad",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE) + guides(color = guide_colorbar(title = "Average Scaled \nExpression"))
ggsave(filename = file.path(PATH, "results/final_figures/mislabeled_broad_markers.png"), height = 4, width = 6)
```

```{r}
strom_genes <- c("COL1A1", "COL1A2", "ENG")
epi_genes <- c("EPCAM", "KRT8","KRT18")
imm_genes <- c("PTPRC", "CD68", "CD3D", "CD3E")
all_markers <- c(strom_genes, imm_genes, epi_genes)
DotPlot_scCustom(seurat_object = mislabeled_subset,
                 features = all_markers, group.by="author_broad",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE) + guides(color = guide_colorbar(title = "Average Scaled \nExpression"))
ggsave(filename = file.path(PATH, "results/final_figures/mislabeled_author_broad_markers.png"), height = 4, width = 6)
```



# Figure 3 

## ComplexHeatmap
```{r}
combined_grouped_df <- readRDS(file.path(PATH, "results/annotation/epi/epi_scores.rds"))
```

```{r}
minmax_scale <- function(x) {
  (x - min(x)) / (max(x) - min(x))
}
# Heatmap without last four clusters
heatmap_dat <- combined_grouped_df %>% 
  dplyr::select(-c(prop_pluri, prop_toti)) %>%
  tibble::column_to_rownames(var = "RNA_snn_res.0.1")
heatmap_dat <- heatmap_dat[as.character(setdiff(0:22, c(9,19,12,21,7,10,11))),]
heatmap_dat <- heatmap_dat[as.character(c(0,14,20,1,22,17,6,5,8,15,18,3,16,13,2,4)),]
heatmap_raw <- heatmap_dat
heatmap_dat[,-c(1:8, 10:12)] <- apply(heatmap_dat[,-c(1:8, 10:12)], 2, minmax_scale)
heatmap_dat <- heatmap_dat %>% as.matrix %>% t
heatmap_raw <- heatmap_raw %>% as.matrix %>% t

heatmap_labels <- rownames(heatmap_dat)
heatmap_labels <- str_remove(heatmap_labels, "HALLMARK_")
heatmap_labels <- str_replace_all(heatmap_labels, pattern = "_", replacement = " ")
heatmap_labels[27:76] <- str_to_sentence(heatmap_labels[27:76])
heatmap_labels[27:76] <- str_replace(heatmap_labels[27:76], "Pi3k" , "PI3K") %>%
  str_replace(., "Wnt", "WNT") %>%
  str_replace(., "Uv", "UV") %>%
  str_replace(., "Tgf beta", "TGF Beta") %>% 
  str_replace(., "Tnfa", "TNFA") %>%
  str_replace(., "akt", "Akt") %>%
  str_replace(., "Mtorc1", "MTORC1") %>%
  str_replace(., "stat", "STAT") %>%
  str_replace(., "Myc", "MYC") %>%
  str_replace(., "jak", "JAK") %>%
  str_replace(., "G2m", "G2M") %>%
  str_replace(., "Il", "IL") %>%
  str_replace(., "E2f", "E2F") %>%
  str_replace(., "Dna", "DNA") %>%
  str_replace(., "Kras", "KRAS")
heatmap_labels[1:15] <- c("Grade 1 (7%)",
                         "Grade 2 (25%)",
                         "Grade 3 (68%)",
                         "ER+ (59%)",
                         "HER2+ (11%)",
                         "TNBC (25%)",
                         "Mean Age",
                         "Prop. Malignant",
                        "Mean Cytotrace",
                        "Prop. Diff",
                        "Prop. Uni",
                        "Prop. Oligo",
                        "Mean Epi. State",
                        "Mean Int. State",
                        "Mean Mes. State")
rownames(heatmap_dat) <- heatmap_labels
saveRDS(heatmap_dat, file = file.path(PATH, "results/annotation/epi/heatmap_dat.rds"))

# Define two color schemes
# col_scores <- colorRamp2(c(-3, 0, 3), c("blue", "white", "red"))
col_scores <- colorRamp2(c(0, 1), c("white", "red"))
col_props <- colorRamp2(c(0, 0.5, 1),  c("#E5F5E0", "#A1D99B", "#31A354"))
col_age <- colorRamp2(c(min(heatmap_dat["Mean Age",], na.rm = TRUE), 
                        median(heatmap_dat["Mean Age",], na.rm = TRUE), 
                        max(heatmap_dat["Mean Age",], na.rm = TRUE)), c(c("#FEE6CE", "#FDAE6B", "#E6550D")))

ht <- Heatmap(heatmap_dat,
              cluster_rows = FALSE,
              cluster_row_slices = FALSE,
              cluster_columns = FALSE,
              cell_fun = function(j, i, x, y, width, height, fill) {
                if (i %in% c(1:6, 8, 10:12)) {
                  grid.rect(x, y, width, height, gp = gpar(fill = col_props(heatmap_dat[i,j]), col = NA))
                } else if (i == 7) {
                  grid.rect(x, y, width, height, gp = gpar(fill = col_age(heatmap_dat[i, j]), col = NA))
                } else {
                  grid.rect(x, y, width, height, gp = gpar(fill = col_scores(heatmap_dat[i, j]), col = NA))
                }
                grid.text(sprintf("%.3f", heatmap_raw[i, j]), x, y, gp = gpar(fontsize = 3))
              },
              row_split = c(rep("Patient", 7), 
                            "Inf.CNV", 
                            rep("Cytotrace", 4), 
                            rep("EMP", 3),
                            rep("HBCA", 11),
                            rep("Hallmark", 50)),
              row_gap = unit(2, "mm"),
              row_title_gp = gpar(fontsize = 5),
              row_names_gp = gpar(fontsize = 5),
              column_names_gp = gpar(fontsize = 5), 
              column_names_rot = 45,
              name = "Scores",
              border = TRUE,
              show_heatmap_legend = FALSE,
              show_row_dend = FALSE)
# Create custom legends
lgd_score <- Legend(col_fun = col_scores, title = "Scaled Scores",labels_gp = gpar(fontsize = 6), title_gp = gpar(fontsize = 7, fontface = "bold"))
lgd_prop <- Legend(col_fun = col_props, title = "Proportions", labels_gp = gpar(fontsize = 6),title_gp = gpar(fontsize = 7, fontface = "bold"))
lgd_age <- Legend(col_fun = col_age, title = "Age", labels_gp = gpar(fontsize = 6),title_gp = gpar(fontsize = 7, fontface = "bold"))

# Draw the heatmap with custom legends

png(file.path(PATH, "results/final_figures/epi/epi_scores_subset_heatmap_minmax_unscaled.png"), width=1500, height=2000, res = 300)
draw(ht, heatmap_legend_list = list(lgd_score, lgd_prop, lgd_age))
dev.off()
```

## K2
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Epi 2025_02_14_11_49_43/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```
```{r}
dgeTable <- getDGETable(K2summary)
dgeTable <- dgeTable %>% 
  dplyr::mutate(group = paste0(node, edge, direction)) %>% 
  dplyr::select(gene, coef, mean, pval, fdr, group) %>% 
  dplyr::mutate(cluster = case_when(group == "D1up" ~ 0,
                                    group == "G1up" ~ 14,
                                    group == "G2up" ~ 20,
                                    group == "O1up" ~ 1,
                                    group == "O2up" ~ 22,
                                    group == "N2up" ~ 17,
                                    group == "L2up" ~ 6,
                                    group == "J2up" ~ 5,
                                    group == "H2up" ~ 8,
                                    group == "M1up" ~ 15,
                                    group == "M2up" ~ 18,
                                    group == "K2up" ~ 3,
                                    group == "I2up" ~ 16,
                                    group == "F1up" ~ 13,
                                    group == "F2up" ~ 2,
                                    group == "C2up" ~ 4,
                                    .default = NA)) %>%
  dplyr::filter(!is.na(cluster)) %>%
  dplyr::arrange(match(cluster, c(0,14,20,1,22,17,6,5,8,15,18,3,16,2,4)))
epi_split <- dgeTable %>% 
  dplyr::group_by(cluster) %>% 
  dplyr::arrange(fdr) %>%
  dplyr::slice(1:100) %>%
  dplyr::group_split() %>%
  setNames(unique(dgeTable$cluster))
sorted_names <- as.character(sort(as.numeric(names(epi_split))))
epi_split <- epi_split[sorted_names]

# Create a new workbook
library(openxlsx)
wb <- createWorkbook()

# Add each group as a separate worksheet
for (cluster in names(epi_split)) {
  addWorksheet(wb, sheetName = paste0("epi_", cluster))
  writeData(wb, sheet = paste0("epi_", cluster), x = epi_split[[cluster]])
}

# Save the workbook
saveWorkbook(wb, file.path(PATH, "results/clustering/k2_clusters.xlsx"), overwrite = TRUE)
```

```{r}
polychrome <- DiscretePalette_scCustomize(num_colors = 30, palette = "polychrome")
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")
all_nodes_labels[is.na(all_nodes_labels)] <- polychrome
all_nodes_labels[which((all_nodes_labels %in% setdiff(0:22, c(9,19,12,21,7,10,11))))] <- polychrome
all_nodes_labels[nchar(all_nodes_labels) == 1] <- "#000000"
k2_epi_dend <- K2dendrogram %>% set("branches_col", all_nodes_labels) %>% set("labels_cex", 1)
k2_epi_dend_gg <- as.ggdend(k2_epi_dend)
ggplot(k2_epi_dend_gg, horiz = FALSE)
ggsave(file.path(PATH, "results/final_figures/epi/k2_epi.png"), width = 8, height = 6)
```

## RF
```{r}
epi_data <- readRDS(file.path(PATH, "results/annotation/epi/scores_cell.rds"))
epi_data <- epi_data %>% dplyr::filter(Cluster %in% setdiff(0:22, c(9,19,12,21,7,10,11)))
epi_data$Cluster <- droplevels(epi_data$Cluster)
epi_data$Cytotrace_Class <- NULL
epi_data$Subtype <- NULL
epi_data$`Cell Id` <- NULL
epi_data$InferCNV_Score <- NULL
epi_data$InferCNV_Malig <- epi_data$InferCNV_Malig*1
epi_data <- dummy_cols(epi_data, select_columns = c("Pam50"), 
                       remove_selected_columns = TRUE)
colnames(epi_data)[9:19] <- paste0(colnames(epi_data)[9:19], " (HBCA)")
colnames(epi_data)[20:69] <- paste0(colnames(epi_data)[20:69], " (Hall.)")
colnames(epi_data) <- str_replace_all(colnames(epi_data), "Cytotrace_Score", replacement = "Cyto. Score")
colnames(epi_data) <- str_replace_all(colnames(epi_data), "Pam50_", replacement = "")
colnames(epi_data) <- str_replace_all(colnames(epi_data), "Hallmark ", replacement = "")
colnames(epi_data)[70:74] <- paste0(colnames(epi_data)[70:74], " (PAM50)")
rf_all_clusters <- readRDS(file.path(PATH, "results/annotation/epi/rf_all_clusters.rds"))
rf_k2_1_clusters <- readRDS(file.path(PATH, "results/annotation/epi/rf_k2_1_clusters.rds"))
rf_k2_2_clusters <- readRDS(file.path(PATH, "results/annotation/epi/rf_k2_2_clusters.rds"))
rf_k2_3_clusters <- readRDS(file.path(PATH, "results/annotation/epi/rf_k2_3_clusters.rds"))

all_features <- colnames(epi_data %>% dplyr::select(-Cluster))
```

### Combined heatmap
```{r}
rf_k2_multi <- c(rf_k2_1_clusters, rf_k2_2_clusters, rf_k2_3_clusters)

all_only <- lapply(rf_k2_multi, function(x) x[["all"]][["imp"]])

binary_matrix <- sapply(all_only, function(features) {
  all_features %in% features
})
rownames(binary_matrix) <- all_features
heatmap_data <- binary_matrix * 1
colnames(heatmap_data) <- str_replace(colnames(heatmap_data), "_", "~")
heatmap_data <- heatmap_data[,c(2,1,5,4,8,6,3,7,12,19,21,11,16,13,20,22,17,14,18,9,10,15)]

all_acc <- lapply(rf_k2_multi, function(x) x[["all"]][["acc"]])
all_acc <- all_acc %>% unlist %>% unname
column_ha <- HeatmapAnnotation(
  barplot = anno_barplot(all_acc),
  height = unit(6, "mm"),
  annotation_label = "RF OOB Acc."
)

# Sorting rows
all_feats <- all_only %>% unlist %>% unname
sorted_feats <- all_feats[!duplicated(all_feats)]
heatmap_data <- heatmap_data[sorted_feats,]
heatmap_data <- heatmap_data[rowSums(heatmap_data) > 0, ]

epi_data$k2_meta_1 <- with(epi_data, case_when(Cluster %in% c(13,2,4) ~ "13~4",
                                               Cluster %in% c(0,14,20,1,22,17,6,5,8,15,18,3,16) ~ "0~16",
                                               .default = as.character(Cluster)))
epi_data_1 <- epi_data %>% dplyr::select(-Cluster) %>% dplyr::group_by(k2_meta_1) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("k2_meta_1") 
epi_data_1 <- epi_data_1[colnames(heatmap_data)[1:2],rownames(heatmap_data)] %>% t

epi_data <- epi_data %>% dplyr::select(-k2_meta_1)
epi_data$k2_meta_2 <- with(epi_data, case_when(Cluster %in% c(13,2) ~ "13~2",
                                               Cluster %in% c(15,18,3,16) ~ "15~16",
                                               Cluster %in% c(1,22,17,6,5) ~ "1~5",
                                               Cluster %in% c(0,14,20) ~ "0~20",
                                               .default = as.character(Cluster)))
epi_data_2 <- epi_data %>% dplyr::select(-Cluster) %>% dplyr::group_by(k2_meta_2) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("k2_meta_2")
epi_data_2 <- epi_data_2[colnames(heatmap_data)[3:8],rownames(heatmap_data)] %>% t

epi_data <- epi_data %>% dplyr::select(-k2_meta_2)
epi_data$k2_meta_3 <- with(epi_data, case_when(Cluster %in% c(1,22,17) ~ "1~17",
                                               .default = as.character(Cluster)))
epi_data_3 <- epi_data %>% dplyr::select(-Cluster) %>% dplyr::group_by(k2_meta_3) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("k2_meta_3")
epi_data_3 <- epi_data_3[colnames(heatmap_data)[9:22],rownames(heatmap_data)] %>% t

epi_data_mean <- cbind(epi_data_1, epi_data_2, epi_data_3)
# Create the heatmap
cell_size <- unit(3, "mm")  # Adjust this value to increase/decrease cell size

ht <- Heatmap(heatmap_data,
              top_annotation = column_ha,
              name = "Presence",
              border=TRUE,
              width = ncol(heatmap_data) * cell_size,
              height = nrow(heatmap_data) * cell_size,
              cell_fun = function(j, i, x, y, width, height, fill) {
                if(heatmap_data[i,j] == 0) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "white"))
                } else if(epi_data_mean[i,j] < mean(epi_data_mean[i,])) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "blue"))
                } else if(epi_data_mean[i,j] > mean(epi_data_mean[i,])){
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "salmon"))
                }
              },
              column_split = factor(c(rep("Level 1", 2), 
                            rep("Level 2", 6), 
                            rep("Level 3", 14)), levels = c("Level 1", "Level 2", "Level 3")),
              column_title = c("Level 1", "Level 2", "Level 3"),
              column_gap = unit(2, "mm"),
              row_names_gp = gpar(fontsize = 8),
              column_names_gp = gpar(fontsize = 8),
              column_title_gp = gpar(fontsize = 10),
              column_title_rot = 30,
              column_names_rot = 60,
              row_title = "Features",
              cluster_columns = FALSE,
              cluster_rows = FALSE,
              show_row_names = TRUE,
              show_column_names = TRUE,
              show_heatmap_legend = FALSE)
# Create the legend
lgd <- Legend(
  labels = c("High", "Low"),
  title = "Scores",
  legend_gp = gpar(fill = c("salmon", "blue")),
  grid_height = unit(3, "mm"),
  grid_width = unit(3, "mm")
)
png(file.path(PATH, "results/final_figures/epi/k2_all_heatmap_sc.png"), width=2000, height=1500, res = 300)
draw(ht, 
     heatmap_legend_list = list(lgd))
dev.off()
```


### All Clusters
```{r}
# Create a binary matrix from the list
all_only <- lapply(rf_all_clusters, function(x) x[["all"]][["imp"]])
binary_matrix <- sapply(all_only, function(features) {
  all_features %in% features
})
rownames(binary_matrix) <- all_features
#colnames(binary_matrix) <- 0:14
heatmap_data <- binary_matrix * 1

# Barplot annotation
all_acc <- lapply(rf_all_clusters, function(x) x[["all"]][["acc"]])
all_acc <- all_acc %>% unlist %>% unname
column_ha <- HeatmapAnnotation(
  barplot = anno_barplot(all_acc),
  height = unit(6, "mm"),
  annotation_label = "RF OOB Acc."
)

# Sorting rows
all_feats <- all_only %>% unlist %>% unname
sorted_feats <- all_feats[!duplicated(all_feats)]
heatmap_data <- heatmap_data[sorted_feats,]
heatmap_data <- heatmap_data[rowSums(heatmap_data) > 0, ]

epi_data_mean <- epi_data %>% dplyr::group_by(Cluster) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("Cluster")
epi_data_mean <- epi_data_mean[colnames(heatmap_data),rownames(heatmap_data)] %>% t
# Create the heatmap
cell_size <- unit(3, "mm")  # Adjust this value to increase/decrease cell size

ht <- Heatmap(heatmap_data,
              top_annotation = column_ha,
              name = "Presence",
              border=TRUE,
              width = ncol(heatmap_data) * cell_size,
              height = nrow(heatmap_data) * cell_size,
              cell_fun = function(j, i, x, y, width, height, fill) {
                if(heatmap_data[i,j] == 0) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "white"))
                } else if(epi_data_mean[i,j] < mean(epi_data_mean[i,])) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "blue"))
                } else if(epi_data_mean[i,j] > mean(epi_data_mean[i,])){
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "salmon"))
                }
              },
              row_names_gp = gpar(fontsize = 8),
              column_names_gp = gpar(fontsize = 8),
              column_title = "Clusters",
              row_title = "Features",
              cluster_columns = FALSE,
              cluster_rows = FALSE,
              show_row_names = TRUE,
              show_column_names = TRUE,
              show_heatmap_legend = FALSE)
# Create the legend
lgd <- Legend(
  labels = c("High", "Low"),
  title = "Scores",
  legend_gp = gpar(fill = c("salmon", "blue")),
  grid_height = unit(6, "mm"),
  grid_width = unit(6, "mm")
)
png(file.path(PATH, "results/final_figures/epi/all_features_heatmap_sc.png"), width=1500, height=2000, res = 300)
draw(ht, heatmap_legend_list = list(lgd))
dev.off()

```

### K1 Clusters
```{r}
all_features <- colnames(epi_data %>% dplyr::select(-Cluster))

# Create a binary matrix from the list
all_only <- lapply(rf_k2_1_clusters, function(x) x[["all"]][["imp"]])
binary_matrix <- sapply(all_only, function(features) {
  all_features %in% features
})
all_only <- all_only[c("10_4_1_7_5", "3_8_9_2_6_13_11_12_0_14")]
rownames(binary_matrix) <- all_features
#colnames(binary_matrix) <- 0:14
heatmap_data <- binary_matrix * 1
colnames(heatmap_data) <- c("3~14", "10~5")
heatmap_data <- heatmap_data[,c("10~5","3~14")]
# Barplot annotation
all_acc <- lapply(rf_k2_1_clusters, function(x) x[["all"]][["acc"]])
all_acc <- all_acc %>% unlist %>% unname
column_ha <- HeatmapAnnotation(
  barplot = anno_barplot(all_acc),
  height = unit(6, "mm"),
  annotation_label = "RF OOB Acc."
)

# Sorting rows
all_feats <- all_only %>% unlist %>% unname
sorted_feats <- all_feats[!duplicated(all_feats)]
heatmap_data <- heatmap_data[sorted_feats,]
heatmap_data <- heatmap_data[rowSums(heatmap_data) > 0, ]

epi_data$k2_meta_1 <- with(epi_data, case_when(Cluster %in% c(10,4,1,7,5) ~ "10~5",
                                               Cluster %in% c(3,8,9,2,6,13,11,12,0,14) ~ "3~14",
                                               .default = Cluster))
epi_data_mean <- epi_data %>% dplyr::select(-Cluster) %>% dplyr::group_by(k2_meta_1) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("k2_meta_1")
epi_data_mean <- epi_data_mean[colnames(heatmap_data),rownames(heatmap_data)] %>% t
# Create the heatmap
cell_size <- unit(3, "mm")  # Adjust this value to increase/decrease cell size

ht <- Heatmap(heatmap_data,
              top_annotation = column_ha,
              name = "Presence",
              border=TRUE,
              width = ncol(heatmap_data) * cell_size,
              height = nrow(heatmap_data) * cell_size,
              cell_fun = function(j, i, x, y, width, height, fill) {
                if(heatmap_data[i,j] == 0) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "white"))
                } else if(epi_data_mean[i,j] < mean(epi_data_mean[i,])) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "blue"))
                } else if(epi_data_mean[i,j] > mean(epi_data_mean[i,])){
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "salmon"))
                }
              },
              row_names_gp = gpar(fontsize = 8),
              column_names_gp = gpar(fontsize = 8),
              column_names_rot = 60,
              column_title = "Clusters",
              row_title = "Features",
              cluster_columns = FALSE,
              cluster_rows = FALSE,
              show_row_names = TRUE,
              show_column_names = TRUE,
              show_heatmap_legend = FALSE)
# Create the legend
lgd <- Legend(
  labels = c("High", "Low"),
  title = "Scores",
  legend_gp = gpar(fill = c("salmon", "blue")),
  grid_height = unit(3, "mm"),
  grid_width = unit(3, "mm")
)
png(file.path(PATH, "results/final_figures/epi/k2_meta_1_heatmap_sc.png"), width=1000, height=1000, res = 300)
draw(ht, 
     heatmap_legend_list = list(lgd))
dev.off()
```

### K2 Clusters
```{r}
all_features <- colnames(epi_data %>% dplyr::select(-Cluster))

# Create a binary matrix from the list
all_only <- lapply(rf_k2_2_clusters, function(x) x[["all"]][["imp"]])
binary_matrix <- sapply(all_only, function(features) {
  all_features %in% features
})
rownames(binary_matrix) <- all_features
#colnames(binary_matrix) <- 0:14
heatmap_data <- binary_matrix * 1
colnames(heatmap_data) <- c("3~6", "10~7", "11~14", "5", "13")
heatmap_data <-heatmap_data[, c("10~7", "5", "3~6", "13", "11~14")]
all_only <- all_only[c("10_4_1_7","5","3_8_9_2_6", "13", "11_12_0_14")]
# Barplot annotation
all_acc <- lapply(rf_k2_2_clusters, function(x) x[["all"]][["acc"]])
all_acc <- all_acc %>% unlist %>% unname
column_ha <- HeatmapAnnotation(
  barplot = anno_barplot(all_acc),
  height = unit(6, "mm"),
  annotation_label = "RF OOB Acc."
)

# Sorting rows
all_feats <- all_only %>% unlist %>% unname
sorted_feats <- all_feats[!duplicated(all_feats)]
heatmap_data <- heatmap_data[sorted_feats,]
heatmap_data <- heatmap_data[rowSums(heatmap_data) > 0, ]

epi_data <- epi_data %>% dplyr::select(-k2_meta_1)
epi_data$k2_meta_2 <- with(epi_data, case_when(Cluster %in% c(10,4,1,7) ~ "10~7",
                                               Cluster %in% c(3,8,9,2,6) ~ "3~6",
                                               Cluster %in% c(11,12,0,14) ~ "11~14",
                                               .default = Cluster))
epi_data_mean <- epi_data %>% dplyr::select(-Cluster) %>% dplyr::group_by(k2_meta_2) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("k2_meta_2")
epi_data_mean <- epi_data_mean[colnames(heatmap_data),rownames(heatmap_data)] %>% t
# Create the heatmap
cell_size <- unit(3, "mm")  # Adjust this value to increase/decrease cell size

ht <- Heatmap(heatmap_data,
              top_annotation = column_ha,
              name = "Presence",
              border=TRUE,
              width = ncol(heatmap_data) * cell_size,
              height = nrow(heatmap_data) * cell_size,
              cell_fun = function(j, i, x, y, width, height, fill) {
                if(heatmap_data[i,j] == 0) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "white"))
                } else if(epi_data_mean[i,j] < mean(epi_data_mean[i,])) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "blue"))
                } else if(epi_data_mean[i,j] > mean(epi_data_mean[i,])){
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "salmon"))
                }
              },
              row_names_gp = gpar(fontsize = 8),
              column_names_gp = gpar(fontsize = 8),
              column_names_rot = 60,
              column_title = "Clusters",
              row_title = "Features",
              cluster_columns = FALSE,
              cluster_rows = FALSE,
              show_row_names = TRUE,
              show_column_names = TRUE,
              show_heatmap_legend = FALSE)
# Create the legend
lgd <- Legend(
  labels = c("High", "Low"),
  title = "Scores",
  legend_gp = gpar(fill = c("salmon", "blue")),
  grid_height = unit(3, "mm"),
  grid_width = unit(3, "mm")
)
png(file.path(PATH, "results/final_figures/epi/k2_meta_2_heatmap_sc.png"), width=1000, height=1000, res = 300)
draw(ht, heatmap_legend_list = list(lgd))
dev.off()
```

### K3 Clusters
```{r}
all_features <- colnames(epi_data %>% dplyr::select(-Cluster))

# Create a binary matrix from the list
all_only <- lapply(rf_k2_3_clusters, function(x) x[["all"]][["imp"]])
binary_matrix <- sapply(all_only, function(features) {
  all_features %in% features
})
rownames(binary_matrix) <- all_features
#colnames(binary_matrix) <- 0:14
heatmap_data <- binary_matrix * 1
colnames(heatmap_data) <- c("2~6", "1~7", "3~9", "10~4", "0~14", "11~12", "5", "13")
heatmap_data <- heatmap_data[,c("10~4","1~7","5","3~9","2~6","13","11~12","0~14")]
all_only <- all_only[c("10_4","1_7","5","3_9","2_6","13","11_12","0_14")]
# Barplot annotation
all_acc <- lapply(rf_k2_3_clusters, function(x) x[["all"]][["acc"]])
all_acc <- all_acc %>% unlist %>% unname
column_ha <- HeatmapAnnotation(
  barplot = anno_barplot(all_acc),
  height = unit(6, "mm"),
  annotation_label = "RF OOB Acc."
)

# Sorting rows
all_feats <- all_only %>% unlist %>% unname
sorted_feats <- all_feats[!duplicated(all_feats)]
heatmap_data <- heatmap_data[sorted_feats,]
heatmap_data <- heatmap_data[rowSums(heatmap_data) > 0, ]

# epi_data <- epi_data %>% dplyr::select(-k2_meta_2)
epi_data$k2_meta_3 <- with(epi_data, case_when(Cluster %in% c(10,4) ~ "10~4",
                                               Cluster %in% c(1,7) ~ "1~7",
                                               Cluster %in% c(3,8,9) ~ "3~9",
                                               Cluster %in% c(2,6) ~ "2~6",
                                               Cluster %in% c(11,12) ~ "11~12",
                                               Cluster %in% c(0,14) ~ "0~14",
                                               .default = Cluster))
epi_data_mean <- epi_data %>% dplyr::select(-Cluster) %>% dplyr::group_by(k2_meta_3) %>% dplyr::summarise_all(mean, na.rm=TRUE) %>% column_to_rownames("k2_meta_3")
epi_data_mean <- epi_data_mean[colnames(heatmap_data),rownames(heatmap_data)] %>% t
# Create the heatmap
cell_size <- unit(3, "mm")  # Adjust this value to increase/decrease cell size

ht <- Heatmap(heatmap_data,
              top_annotation = column_ha,
              name = "Presence",
              border=TRUE,
              width = ncol(heatmap_data) * cell_size,
              height = nrow(heatmap_data) * cell_size,
              cell_fun = function(j, i, x, y, width, height, fill) {
                if(heatmap_data[i,j] == 0) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "white"))
                } else if(epi_data_mean[i,j] < mean(epi_data_mean[i,])) {
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "blue"))
                } else if(epi_data_mean[i,j] > mean(epi_data_mean[i,])){
                  grid.rect(x = x, y = y, width = width, height = height,
                            gp = gpar(col = "black", fill = "salmon"))
                }
              },
              row_names_gp = gpar(fontsize = 8),
              column_names_gp = gpar(fontsize = 8),
              column_names_rot = 60,
              column_title = "Clusters",
              row_title = "Features",
              cluster_columns = FALSE,
              cluster_rows = FALSE,
              show_row_names = TRUE,
              show_column_names = TRUE,
              show_heatmap_legend = FALSE)
# Create the legend
lgd <- Legend(
  labels = c("High", "Low"),
  title = "Scores",
  legend_gp = gpar(fill = c("salmon", "blue")),
  grid_height = unit(3, "mm"),
  grid_width = unit(3, "mm")
)
png(file.path(PATH, "results/final_figures/epi/k2_meta_3_heatmap_sc.png"), width=1000, height=1000, res = 300)
draw(ht, heatmap_legend_list = list(lgd))
dev.off()
```


# Figure 5 Immune Cell Type Diversity

```{r}
imm_subset <- readRDS(file.path(PATH, "data/sc/imm_rpca_sub_clean.rds"))
# Idents(imm_subset) <- imm_subset$RNA_snn_res.0.6
Idents(imm_subset) <- imm_subset$cluster_annot_sub
imm_subset$cluster_annot_sub <- str_replace_all(imm_subset$cluster_annot_sub, "_", " ")
# Idents(imm_subset) <- factor(Idents(imm_subset),
#                                      levels = levels(Idents(imm_subset))[order(as.numeric(levels(Idents(imm_subset))))])
```

## Donors/Entropy
```{r}
donor_data <- imm_subset@meta.data %>% 
  dplyr::group_by(RNA_snn_res.0.6) %>% 
  dplyr::summarise(
    distinct_count = n_distinct(donor), 
    entropy = {
      p <- table(donor) / n()
      if(n_distinct(donor) > 1) {
        -sum(p * log2(p)) / log2(n_distinct(donor))
      } else {
        -sum(p * log2(p))
      }
})
varibow_pal <- DiscretePalette_scCustomize(num_colors = 138, palette = "varibow")
p1 <- imm_subset@meta.data %>% 
  dplyr::count(RNA_snn_res.0.6, donor) %>% 
  dplyr::group_by(RNA_snn_res.0.6) %>%
  dplyr::mutate(unique_donors = n_distinct(donor),
                total_cells = sum(n)) %>%
  ggplot(aes(x = reorder(RNA_snn_res.0.6, n, sum, decreasing = TRUE), fill = donor, y = n)) + 
  geom_col(position = "stack", colour = "black") +
  geom_text(
    aes(y = total_cells, label = unique_donors),
    vjust = -0.5,
    size = 2
  ) + 
  scale_fill_manual(values = varibow_pal) +
  theme(legend.position = "none",
        text = element_text(size = 12),
        axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1)) + 
  labs(x = "Cluster", y = "# Cells", title = "Number of Donors/Cluster")

varibow_pal <- DiscretePalette_scCustomize(num_colors = 31, palette = "varibow")
p2 <- donor_data %>% 
  ggplot(aes(x = reorder(RNA_snn_res.0.6, entropy, decreasing = TRUE), fill = RNA_snn_res.0.6, y = entropy)) +
  geom_col(position = "stack", colour = "black") +
  scale_fill_manual(values = varibow_pal) +
  theme(legend.position = "none",
        text = element_text(size = 12),
        axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1)) + 
  labs(x = "Cluster", y = "Entropy", title = "Entropy of donor proportions")
combined <- cowplot::plot_grid(p1, p2, nrow = 1, ncol = 2)
ggsave(plot = combined, filename = file.path(PATH, "results/final_figures/donors_entropy_imm.png"), width = 9, height = 4)
```

```{r}
Idents(imm_subset) <- imm_subset$combined.sub
Cluster_Highlight_Plot(imm_subset,
                       cluster_name = c("mac_3", "mac_8", "mac_11"),
                       reduction = "umap.rpca",
                       group.by = "combined.sub",
                       label = TRUE, 
                       label.size = 2,
                       repel = TRUE,
                       label.box = TRUE,
                       raster = FALSE) + labs(title = NULL, x = "UMAP 1", y = "UMAP 2")
```

## Final Cluster Annot
```{r}
DimPlot_scCustom(imm_subset,
                 reduction = "umap.rpca",
                 group.by = "cluster_annot_sub",
                 label = TRUE, 
                 label.size = 4,
                 repel = TRUE,
                 label.box = TRUE,
                 raster = FALSE) + labs(title = NULL, x = "UMAP 1", y = "UMAP 2")
ggsave(filename = file.path(PATH, "results/final_figures/cluster_annot_imm_final_big.png"), width = 9, height = 6)
```

## K2 
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Imm 2025_09_03_20_15_46/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
labels(K2dendrogram) <- str_replace_all(labels(K2dendrogram), "_", " ")
labels(K2dendrogram)[labels(K2dendrogram) == "Mono NC"] <- "Mac/Mono"
```

```{r}
# cluster_annot_df <- K2summary@colData %>% 
#   as.data.frame %>% 
#   dplyr::count(cluster_annot, RNA_snn_res.0.6) 
# cluster_annot_list <- as.list(cluster_annot_df$cluster_annot)
# names(cluster_annot_list) <- cluster_annot_df$RNA_snn_res.0.6
```

```{r}
# K2dendrogram <- K2dendro(K2summary)
# curr_labels <- K2dendrogram %>% labels
# new_labels <- cluster_annot_list[curr_labels] %>% unname %>% unlist
# K2dendrogram <- K2dendrogram %>% set("labels", new_labels)
```

```{r}
polychrome <- DiscretePalette_scCustomize(num_colors = n_distinct(labels(K2dendrogram)), palette = "polychrome")
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")
all_nodes_labels[is.na(all_nodes_labels)] <- polychrome
all_nodes_labels[which((all_nodes_labels %in% labels(K2dendrogram)))] <- polychrome
all_nodes_labels[nchar(all_nodes_labels) <= 2] <- "#000000"
K2dendrogram %>% set("branches_col", all_nodes_labels)  %>% set("labels_cex", 0.7) %>% plot
```

## Dotplot
```{r}
t_nk_subset <- subset(imm_subset, subset = RNA_snn_res.0.6 %in% c(1,10,12,14,18,2,25,27,3,5,6,9))
b_plasma_subset <- subset(imm_subset, subset = RNA_snn_res.0.6 %in% c(24,28,4,7))
myeloid_subset <- subset(imm_subset, subset = RNA_snn_res.0.6 %in% c(0,11,16,17,19,21,23,8))
```

```{r}
t_nk_subset$cluster_annot_sub <- factor(t_nk_subset$cluster_annot_sub, levels = c("CD4 Naive", "CD4 Tem", "CD4 Tfh", "CD4 Th", "CD4 Treg", "CD8 Isg", "CD8 Tem", "CD8 Tex", "NK Cyto.", "NK rNK", "NK", "T Prolif."))
b_plasma_subset$cluster_annot_sub <- factor(b_plasma_subset$cluster_annot_sub, levels = c("B Cell", "B ACB", "B GCB", "B IFIT", "B Naive", "Plasma IgG"))
myeloid_subset$cluster_annot_sub <- factor(myeloid_subset$cluster_annot_sub, levels = c("Mac Anti.","Mac ES","Mac IFN", "Mac LA", "Mac RTM IFN", "Mac RTM LA", "Mac RTM MT", "Mac/Mono", "cDC2","cDC1","pDC","mDC","Mast"))

t_nk_sigs <- c("CCR7","PASK","LEF1","LMNA","UBE2S","FOSB","CXCL13","GNG4","NMB","CD200","MUCL1","TNFSF13B","IL4I1","FOXP3","IL1R2","RTKN2","IL2RA","TNFRSF4","IFIT1","IFIT2","IFIT3","RSAD2","GZMK","EOMES","CRTAM","CCL4L2","VCAM1","LAG3","PDCD1","TIGIT","GZMB","KLRF1","FCER1G","FCGR3A","XCL1","NR4A1","DNAJB1","GNLY","MKI67","TYMS","TOP2A") %>% rev

b_plasma_sigs <- c("MS4A1","CD74","HLA-DRA","CCR7","CD69","NR4A2","IL7R","GAPDH","PFN1", "IFI44L","STAT1","IL4R","FCER2","TCL1A","IGHG2","IGLV3-1","IGHG1") %>% rev

myeloid_sigs <- c("CKS1B","MKI67","STMN1","TYMS","LPL","CYP27A1","CHIT1","CXCL10","FGL2","FCN1","PLIN2","SPP1","S100A8","IL4I1","CXCL9","PLD4","C3","NR4A2","MRC1","FOLR2","PLTP","IFITM1","C1QB","C1QA","FCER1A","CLEC10A","CD1C","CLEC9A","XCR1","CLEC4C","LILRA4","IL3RA","TCL1A","LAMP3","CCR7","CPA3","TPSAB1","MS4A2") %>% rev
```

```{r}
DotPlot_scCustom(seurat_object = t_nk_subset,
                 features = t_nk_sigs, group.by="cluster_annot_sub",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE) + guides(color = guide_colorbar(title = "Average Scaled \nExpression"))
ggsave(filename = file.path(PATH, "results/dotplots/t_nk_canonical_markers.png"), height = 4, width = 12)
```

```{r}
DotPlot_scCustom(seurat_object = b_plasma_subset,
                 features = b_plasma_sigs, group.by="cluster_annot_sub",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE) + guides(color = guide_colorbar(title = "Average Scaled \nExpression"))
ggsave(filename = file.path(PATH, "results/dotplots/b_plasma_canonical_markers.png"), height = 4, width = 9)
```

```{r}
DotPlot_scCustom(seurat_object = myeloid_subset,
                 features = myeloid_sigs, group.by="cluster_annot_sub",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE) + guides(color = guide_colorbar(title = "Average Scaled \nExpression"))
ggsave(filename = file.path(PATH, "results/dotplots/myeloid_canonical_markers.png"), height = 4, width = 11)
```

## Sankey 
```{r}
df <- imm_subset@meta.data %>% 
  dplyr::mutate(cluster_major = case_when(str_detect(cluster_annot_sub, "CD4|CD8|NK|Plasma|B") ~ "Lymphoid",
                                          str_detect(cluster_annot_sub, "Mac|Mast|DC|Mono") ~ "Myeloid",
                                          str_detect(cluster_annot_sub, "T Prolif.") ~ "Lymphoid",
                                          str_detect(cluster_annot_sub, "Mac Prolif.") ~ "Myeloid")) %>%
  dplyr::select(cluster_broad, cluster_major, cluster_annot_sub) %>% 
  dplyr::rename("Broad" = cluster_broad, "Level 1" = cluster_major, "Level 2" = cluster_annot_sub) %>% 
  ggsankey::make_long("Broad", "Level 1", "Level 2")
df <- df %>% 
  dplyr::mutate(node = factor(node, levels = c("Immune",
                                               "Lymphoid", 
                                               "B_ACB", "B_Cell", "B_GCB", "B_IFIT", "B_Naive", "Plasma IgG",
                                               "CD4_Naive", "CD4_Tem", "CD4_Tfh", "CD4_Th", "CD4_Treg", "CD8_Isg", "CD8_Tem", "CD8_Tex", "NK", "NK_Cyto.", "NK_rNK", "T Prolif.",
                                               "Myeloid",
                                               "cDC1", "cDC2",  "mDC", "pDC", "Mac_Anti.", "Mac_ES", "Mac_IFN", "Mac_RTM_IFN",
                                               "Mac_RTM_LA", "Mac_RTM_MT", "Mac/Mono")),
                next_node = factor(next_node, levels = c("Lymphoid", 
                                               "B Cell", "Plasma IgG",
                                               "CD4 Naive", "CD4 Tem", "CD4 Tfh", "CD4 Th", "CD4 Treg", "CD8 Isg", "CD8 Tem", "CD8 Tex", "NK", "T Prolif.",
                                               "Myeloid",
                                               "cDC1", "cDC2",  "mDC", "pDC", "Mac Col.", "Mac Lipo", "Mac Prolif.", "Mast")))
```

```{r}
ggplot(df, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = node, label = node)) +
  geom_sankey(flow.alpha = .6,
              node.color = "gray30",
              smooth = 4) +
  geom_sankey_label(size = 3, color = "white", fill = "gray40") +
  scale_fill_viridis_d(drop = FALSE) +
  theme_sankey(base_size = 18) +
  labs(x = NULL,
       title = "Immune Cell Diversity") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5)) 
ggsave(file.path(PATH, "results/final_figures/imm_annot.png"), width = 6, height = 6)
```


# Figure 6 Stromal Cell Diversity
```{r}
strom_subset <- readRDS(file.path(PATH, "data/sc/strom_rpca_subset.rds"))
Idents(strom_subset) <- strom_subset$RNA_snn_res.0.4
```

## Final Cluster Annotation
```{r}
DimPlot_scCustom(strom_subset,
                 reduction = "umap.rpca",
                 group.by = "cluster_annot",
                 label = TRUE, 
                 label.size = 4,
                 repel = TRUE,
                 label.box = TRUE,
                 raster = FALSE) + labs(title = NULL, x = "UMAP 1", y = "UMAP 2")
ggsave(filename = file.path(PATH, "results/final_figures/cluster_annot_strom_final_big.png"), width = 6, height = 5)
```

## Donors/Entropy
```{r}
donor_data <- strom_subset@meta.data %>% 
  dplyr::group_by(RNA_snn_res.0.4) %>% 
  dplyr::summarise(
    distinct_count = n_distinct(donor), 
    entropy = {
      p <- table(donor) / n()
      if(n_distinct(donor) > 1) {
        -sum(p * log2(p)) / log2(n_distinct(donor))
      } else {
        -sum(p * log2(p))
      }
})
varibow_pal <- DiscretePalette_scCustomize(num_colors = 138, palette = "varibow")
p1 <- strom_subset@meta.data %>% 
  dplyr::count(RNA_snn_res.0.4, donor) %>% 
  dplyr::group_by(RNA_snn_res.0.4) %>%
  dplyr::mutate(unique_donors = n_distinct(donor),
                total_cells = sum(n)) %>%
  ggplot(aes(x = reorder(RNA_snn_res.0.4, n, sum, decreasing = TRUE), fill = donor, y = n)) + 
  geom_col(position = "stack", colour = "black") +
  geom_text(
    aes(y = total_cells, label = unique_donors),
    vjust = -0.5,
    size = 2
  ) + 
  scale_fill_manual(values = varibow_pal) +
  theme(legend.position = "none",
        text = element_text(size = 12),
        axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1)) + 
  labs(x = "Cluster", y = "# Cells", title = "Number of Donors/Cluster")

varibow_pal <- DiscretePalette_scCustomize(num_colors = 31, palette = "varibow")
p2 <- donor_data %>% 
  ggplot(aes(x = reorder(RNA_snn_res.0.4, entropy, decreasing = TRUE), fill = RNA_snn_res.0.4, y = entropy)) +
  geom_col(position = "stack", colour = "black") +
  scale_fill_manual(values = varibow_pal) +
  theme(legend.position = "none",
        text = element_text(size = 12),
        axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1)) + 
  labs(x = "Cluster", y = "Entropy", title = "Entropy of donor proportions")
combined <- cowplot::plot_grid(p1, p2, nrow = 1, ncol = 2)
ggsave(plot = combined, filename = file.path(PATH, "results/final_figures/donors_entropy_strom.png"), width = 9, height = 4)
```

## K2 
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Strom 2025_02_14_10_20_28/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
cluster_annot_df <- K2summary@colData %>% 
  as.data.frame %>% 
  dplyr::count(cluster_annot, RNA_snn_res.0.4) 
cluster_annot_list <- as.list(cluster_annot_df$cluster_annot)
names(cluster_annot_list) <- cluster_annot_df$RNA_snn_res.0.4
```

```{r}
K2dendrogram <- K2dendro(K2summary)
curr_labels <- K2dendrogram %>% labels
new_labels <- cluster_annot_list[curr_labels] %>% unname %>% unlist
K2dendrogram <- K2dendrogram %>% set("labels", new_labels)
```

```{r}
polychrome <- DiscretePalette_scCustomize(num_colors = n_distinct(cluster_annot_df$cluster_annot), palette = "polychrome")
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")
all_nodes_labels[is.na(all_nodes_labels)] <- polychrome
all_nodes_labels[which((all_nodes_labels %in% unname(cluster_annot_list)))] <- polychrome
all_nodes_labels[nchar(all_nodes_labels) == 1] <- "#000000"
k2_strom_dend <- K2dendrogram %>% set("branches_col", all_nodes_labels)  %>%  set("labels_cex", 0.7)
k2_strom_dend %>% plot()
```

## Dot Plot
```{r}
pan_cancer_stromal_sigs <- readRDS(file.path(PATH, "data/signatures/stromal/ye_2024/pan_cancer_stromal_sigs.rds"))
wu_strom_sigs <- readRDS(file.path(PATH, "data/signatures/stromal/wu_embo_2020/strom_sigs.rds"))
# dotplot_sigs <- c(wu_strom_sigs["icafs"], pan_cancer_stromal_sigs[c("CA12+ CAFs", "COL11A1+ CAFs", "SFRP4+ CAFs",
#                                                                     "Arterial ECs", "Capillaries ECs", "Immature ECs",
#                                                                     "ISG15+ ECs", "Lymphatics ECs", "Venous ECs",
#                                                                     "CCL19+ PCs", "ECM PCs")])
# dotplot_sigs$VSMC <- c("MYH11", "RERGL")
# dotplot_sigs <- dotplot_sigs[c("SFRP4+ CAFs", "COL11A1+ CAFs", "CA12+ CAFs", "icaf",
#                                "Arterial ECs", "Capillaries ECs", "Immature ECs", "ISG15+ ECs", "Lymphatics ECs", "Venous ECs",
#                                "ECM PCs", "CCL19+ PCs", "VSMC")] %>% rev
# dotplot_sigs <- lapply(dotplot_sigs, function(x) x[x %in% rownames(strom_subset)]) %>% unlist %>% unname
# dotplot_sigs <- dotplot_sigs[!duplicated(dotplot_sigs)]
dotplot_sigs <- c("MYH11", "RERGL", "MKI67", "TOP2A", "STMN1", "HIGD1B", "COL4A1", "COL4A2",
                  "RGS5" , "CDH6" , "GJC1", "ACKR1", "SELP", "ZNF385D", "MRC1", "PDPN", "MMRN1", "ESM1", "FOLH1","PLVAP", "VWA1", "RBP7", "RGCC" , "TMEM88", "SEMA3G", "GJA5",
                  "PI16" , "PCOLCE2", "LAMP5", "CST1", "CST2", "HSPB6" , "PTGDS", "COL11A1", "SDC1", "CA12", "CA9", "SLC2A1")
# strom_subset$cluster_annot <- factor(strom_subset$cluster_annot, levels = c("CAFs (CA12+)", "CAFs (COL11A+)", "CAFs (DPT+)", "CAFs (LAMP5)", "CAFs (PI16+)",
#                                                                             "Endo Arter.", "Endo Capil.", "Endo Imm.", "Endo Lymph.", "Endo Ven.", "Myofibroblast", 
#                                                                             "PCs (ECM)", "Prolif. Stromal", "VSMC"))
DotPlot_scCustom(seurat_object = strom_subset,
                 features = dotplot_sigs, group.by="cluster_annot",
                 colors_use = viridis_plasma_dark_high,
                 x_lab_rotate = TRUE)+ guides(color = guide_colorbar(title = "Average Scaled \nExpression"))
# ggsave(filename = file.path(PATH, "results/dotplots/strom_canonical_markers_full.png"), height = 4, width = 22)
ggsave(filename = file.path(PATH, "results/dotplots/strom_canonical_markers_2_4genes.png"), height = 4, width = 11)
```

## Sankey
```{r}
df <- strom_subset@meta.data %>% 
  dplyr::mutate(cluster_major = case_when(str_detect(cluster_annot, "CAF") ~ "Fibroblasts",
                                          str_detect(cluster_annot, "Myo") ~ "Fibroblasts",
                                          str_detect(cluster_annot, "Endo") ~ "Endothelial",
                                          str_detect(cluster_annot, "PCs") ~ "Mural",
                                          str_detect(cluster_annot, "Prolif") ~ "Prolif",
                                          str_detect(cluster_annot, "VSMC") ~ "Mural")) %>%
  dplyr::select(cluster_broad, cluster_major, cluster_annot) %>% 
  dplyr::rename("Broad" = cluster_broad, "Level 1" = cluster_major, "Level 2" = cluster_annot) %>% 
  ggsankey::make_long("Broad", "Level 1", "Level 2")

df <- df %>%
  dplyr::mutate(node = factor(node, levels = c("Stromal",
                                               "Endothelial",
                                               "Endo Arter.", "Endo Imm.", "Endo Lymph.", "Endo Ven.", "Endo Capil.",
                                               "Fibroblasts",
                                               "CAFs (CA12+)", "CAFs (COL11A1+)", "CAFs (DPT+)", "CAFs (LAMP5)", "CAFs (PI16+)", "Myofibroblast",
                                               "Mural",
                                               "PCs (ECM)", "VSMC",
                                               "Prolif",
                                               "Prolif. Stromal")),
                next_node = factor(next_node, levels = c("Endothelial",
                                                         "Endo Arter.", "Endo Imm.", "Endo Lymph.", "Endo Ven.", "Endo Capil.",
                                                         "Fibroblasts",
                                                         "CAFs (CA12+)", "CAFs (COL11A1+)", "CAFs (DPT+)", "CAFs (LAMP5)", "CAFs (PI16+)", "Myofibroblast",
                                                         "Mural",
                                                         "PCs (ECM)", "VSMC",
                                                         "Prolif",
                                                         "Prolif. Stromal")))
```

```{r}
ggplot(df, aes(x = x, next_x = next_x, node = node, next_node = next_node, fill = factor(node), label = node)) +
  geom_sankey(flow.alpha = .6,
              node.color = "gray30",
              smooth = 4) +
  geom_sankey_label(size = 3, color = "white", fill = "gray40") +
  scale_fill_viridis_d(drop = FALSE) +
  theme_sankey(base_size = 18) +
  labs(x = NULL,
       title = "Stromal Cell Diversity") +
  theme(legend.position = "none",
        plot.title = element_text(hjust = .5)) 
ggsave(file.path(PATH, "results/final_figures/stromal_annot.png"), width = 6, height = 6)
```


# Figure 7 Differential Abundance Analysis

## Imm - Grade (Subtype)
```{r}
sccomp_grade_subtype <- readRDS(file.path(PATH, "results/sccomp/imm/grade_subtype.rds"))
sccomp_grade_subtype_df <- sccomp_grade_subtype %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh")
sccomp_grade_subtype_order <- sccomp_grade_subtype_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_grade_subtype_df$cluster_annot_sub <- str_replace_all(sccomp_grade_subtype_df$cluster_annot_sub, "_", " ")
sccomp_grade_subtype_df
```

```{r}
sccomp_grade_subtype_plot <- sccomp_plot_data(sccomp_grade_subtype_df, annot_col = "cluster_annot_sub")
ggsave(plot = sccomp_grade_subtype_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_subtype_all.png"), width = 6, height = 7)
```

### Combination
```{r}
sccomp_grade_subtype_wang <- readRDS(file.path(PATH, "results/sccomp/imm/wang_2024_grade_subtype.rds"))
sccomp_grade_subtype_wu_natgen <- readRDS(file.path(PATH, "results/sccomp/imm/wu_natgen_2021_grade_subtype.rds"))
sccomp_grade_subtype_pal <- readRDS(file.path(PATH, "results/sccomp/imm/pal_2021_grade_subtype.rds"))

sccomp_grade_subtype_pal$cluster_annot_sub <- str_replace(sccomp_grade_subtype_pal$cluster_annot_sub, "_", " ")
sccomp_grade_subtype_wang$cluster_annot_sub <- str_replace(sccomp_grade_subtype_wang$cluster_annot_sub, "_", " ")
sccomp_grade_subtype_wu_natgen$cluster_annot_sub <- str_replace(sccomp_grade_subtype_wu_natgen$cluster_annot_sub, "_", " ")
sccomp_grade_subtype_wang$c_FDR[sccomp_grade_subtype_wang$c_FDR == 0] <- min(sccomp_grade_subtype_wang$c_FDR[sccomp_grade_subtype_wang$c_FDR > 0])

sccomp_grade_subtype_wang_plot <- sccomp_grade_subtype_wang %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh", order = sccomp_grade_subtype_order) %>% sccomp_plot_data(annot_col = "cluster_annot_sub", sort_y = FALSE)
sccomp_grade_subtype_wu_natgen_plot <- sccomp_grade_subtype_wu_natgen %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh", order = sccomp_grade_subtype_order) %>% sccomp_plot_data(annot_col = "cluster_annot_sub", sort_y = FALSE)
sccomp_grade_subtype_pal_plot <- sccomp_grade_subtype_pal %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh", order = sccomp_grade_subtype_order) %>% sccomp_plot_data(annot_col = "cluster_annot_sub", sort_y = FALSE)
```

```{r}
cowplot::plot_grid(sccomp_grade_subtype_plot + labs(title = "Atlas") + theme(axis.title.x = element_blank(), legend.position = "none"), 
                   sccomp_grade_subtype_pal_plot + labs(title = "Pal 2021")  + theme(axis.title.x = element_blank(), legend.position = "none"), 
                   sccomp_grade_subtype_wang_plot + labs(title = "Wang 2024") + theme(axis.title.x = element_blank(), legend.position = "none"),
                   sccomp_grade_subtype_wu_natgen_plot + labs(title = "Wu Natgen 2021") + theme(axis.title.x = element_blank()),
                   ncol = 4, nrow = 1)
ggsave(file.path(PATH, "results/final_figures/combined_imm_grade_subtype_sccomp_dotplot.png"), width = 24, height = 7, dpi = 600)
ggsave(sccomp_grade_subtype_wang_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_subtype_wang.png"), width = 6, height = 6)
ggsave(sccomp_grade_subtype_pal_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_subtype_pal.png"), width = 6, height = 6)
ggsave(sccomp_grade_subtype_wu_natgen_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_subtype_wu_natgen.png"), width = 6, height = 6)
```


## Imm - Grade (Pam50)
```{r}
sccomp_grade_pam50 <- readRDS(file.path(PATH, "results/sccomp/imm/grade_pam50.rds"))
sccomp_grade_pam50_df <- sccomp_grade_pam50 %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh")
sccomp_grade_pam50_df$cluster_annot_sub <- str_replace(sccomp_grade_pam50_df$cluster_annot_sub, "_", " ")
sccomp_grade_pam50_order <- sccomp_grade_pam50_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
```

```{r}
sccomp_grade_pam50_plot <- sccomp_plot_data(sccomp_grade_pam50_df, annot_col = "cluster_annot_sub")
ggsave(plot = sccomp_grade_pam50_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_pam50_all.png"), width = 6, height = 7)
```

### Combination
```{r}
sccomp_grade_pam_wang <- readRDS(file.path(PATH, "results/sccomp/imm/wang_2024_pam50_subtype.rds"))
sccomp_grade_pam_wu_natgen <- readRDS(file.path(PATH, "results/sccomp/imm/wu_natgen_2021_pam50_subtype.rds"))
sccomp_grade_pam_pal <- readRDS(file.path(PATH, "results/sccomp/imm/pal_2021_pam50_subtype.rds"))

sccomp_grade_pam_pal$cluster_annot_sub <- str_replace(sccomp_grade_pam_pal$cluster_annot_sub, "_", " ")
sccomp_grade_pam_wang$cluster_annot_sub <- str_replace(sccomp_grade_pam_wang$cluster_annot_sub, "_", " ")
sccomp_grade_pam_wu_natgen$cluster_annot_sub <- str_replace(sccomp_grade_pam_wu_natgen$cluster_annot_sub, "_", " ")
sccomp_grade_pam_wang$c_FDR[sccomp_grade_pam_wang$c_FDR == 0] <- min(sccomp_grade_pam_wang$c_FDR[sccomp_grade_pam_wang$c_FDR > 0])

sccomp_grade_pam_wang_plot <- sccomp_grade_pam_wang %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh", order = sccomp_grade_pam50_order) %>% sccomp_plot_data(annot_col = "cluster_annot_sub", sort_y = FALSE)
sccomp_grade_pam_wu_natgen_plot <- sccomp_grade_pam_wu_natgen %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh", order = sccomp_grade_pam50_order) %>% sccomp_plot_data(annot_col = "cluster_annot_sub", sort_y = FALSE)
sccomp_grade_pam_pal_plot <- sccomp_grade_pam_pal %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "grade_binhigh", order = sccomp_grade_pam50_order) %>% sccomp_plot_data(annot_col = "cluster_annot_sub", sort_y = FALSE)
```

```{r}
cowplot::plot_grid(sccomp_grade_pam50_plot + labs(title = "Atlas") + theme(axis.title.x = element_blank(), legend.position = "none"), 
                   sccomp_grade_pam_pal_plot + labs(title = "Pal 2021")  + theme(axis.title.x = element_blank(), legend.position = "none"), 
                   sccomp_grade_pam_wang_plot + labs(title = "Wang 2024") + theme(axis.title.x = element_blank(), legend.position = "none"),
                   sccomp_grade_pam_wu_natgen_plot + labs(title = "Wu Natgen 2021") + theme(axis.title.x = element_blank()),
                   ncol = 4, nrow = 1)
ggsave(file.path(PATH, "results/final_figures/combined_imm_grade_pam_sccomp_dotplot.png"), width = 20, height = 7, dpi = 600)
ggsave(sccomp_grade_pam_wang_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_pam50_wang.png"), width = 6, height = 6)
ggsave(sccomp_grade_pam_pal_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_pam50_pal.png"), width = 6, height = 6)
ggsave(sccomp_grade_pam_wu_natgen_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_grade_pam50_wu_natgen.png"), width = 6, height = 6)
```

## Imm - Age (Pam50 + Grade)
```{r}
sccomp_age_pam50 <- readRDS(file.path(PATH, "results/sccomp/imm/grade_pam50_v.rds"))
sccomp_age_pam50_df <- sccomp_age_pam50 %>% sccomp_prep_data(., param = "age")
sccomp_age_pam50_order <- sccomp_age_pam50_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_age_pam50_df
```

```{r}
sccomp_age_pam50_plot <- sccomp_plot_data(sccomp_age_pam50_df, sort_y = )
ggsave(plot = sccomp_age_pam50_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_age_pam50_all.png"), width = 6, height = 6)
```


## Imm - Age (Pam50)
```{r}
sccomp_age_pam50 <- readRDS(file.path(PATH, "results/sccomp/imm/age_pam50_v.rds"))
sccomp_age_pam50_df <- sccomp_age_pam50 %>% sccomp_prep_data(., param = "age")
sccomp_age_pam50_order <- sccomp_age_pam50_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_age_pam50_df$cluster_annot_sub <- str_replace(sccomp_age_pam50_df$cluster_annot_sub, "_", " ")
```

```{r}
sccomp_age_pam50_plot <- sccomp_plot_data(sccomp_age_pam50_df, sort_y = )
ggsave(plot = sccomp_age_pam50_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_age_pam50_all.png"), width = 6, height = 6)
```

## Imm - GSVA
```{r}
do_save <- FALSE
if (do_save) {
  atlas_gsva <- readRDS(file.path(PATH, "data/pseudobulk/combined_data_gsva_imm.rds"))
  gsva_imm_data <- atlas_gsva@assays@data$es %>% t %>% as.data.frame %>% rownames_to_column(var = "donor")
  atlas_metadata <- read.csv(file.path(PATH, "data/metadata/all_metadata.csv"), row.names = NULL)
  gsva_imm_data$donor <- str_replace_all(gsva_imm_data$donor, "-", "_")
  gsva_imm_data <- dplyr::left_join(gsva_imm_data, atlas_metadata %>% dplyr::select(donor, age, pam50, batch), by = "donor")
  celltypes <- rownames(atlas_gsva)
  mus <- c()
  stds <- c()
  fdrs <- c()
  for (celltype in celltypes) {
    celltype_lm <- lmerTest::lmer(data = gsva_imm_data, formula = paste0("`", celltype, "`", " ~ age + pam50 + (1|batch)"))
    coef_df <- summary(celltype_lm)$coef
    coef_df_mu <- coef_df["age", "Estimate"]
    coef_df_std <- coef_df["age", "Std. Error"]
    coef_df_p_val <- coef_df["age", "Pr(>|t|)"]
    mus <- c(mus, coef_df_mu)
    stds <- c(stds, coef_df_std)
    fdrs <- c(fdrs, coef_df_p_val)
  }
  regression_data <- data.frame(celltypes = celltypes, mu = mus, se = stds, fdr = fdrs)
  regression_data$fdr <- p.adjust(regression_data$fdr, method = "fdr")
  saveRDS(regression_data, file.path(PATH, "results/regression_data.rds"))
} else {
  regression_data <- readRDS(file.path(PATH, "results/regression_data.rds"))
}
```

```{r}
dot_plot(regression_data, y_label = "celltypes", x_intercept = 0)
ggsave(file.path(PATH, "results/final_figures/imm_gsva.png"), height = 12, width = 6)
```


## Imm - luma
```{r}
sccomp_luma <- readRDS(file.path(PATH, "results/sccomp/imm/pam_luma.rds"))
sccomp_luma_df <- sccomp_luma %>% sccomp_prep_data(., param = "pam_lumaTRUE")
sccomp_luma_order <- sccomp_luma_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_luma_df$cluster_annot_sub <- str_replace(sccomp_luma_df$cluster_annot_sub, "_", " ")
```

```{r}
sccomp_luma_plot <- sccomp_plot_data(sccomp_luma_df)
ggsave(plot = sccomp_luma_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_luma_all.png"), width = 6, height = 6)
```

## Imm - lumb
```{r}
sccomp_lumb <- readRDS(file.path(PATH, "results/sccomp/imm/pam_lumb.rds"))
sccomp_lumb_df <- sccomp_lumb %>% sccomp_prep_data(., param = "pam_lumbTRUE")
sccomp_lumb_order <- sccomp_lumb_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_lumb_df$cluster_annot_sub <- str_replace(sccomp_lumb_df$cluster_annot_sub, "_", " ")
sccomp_lumb_df$c_FDR[sccomp_lumb_df$c_FDR == 0] <- min(sccomp_lumb_df$c_FDR[sccomp_lumb_df$c_FDR > 0])
```

```{r}
sccomp_lumb_plot <- sccomp_plot_data(sccomp_lumb_df)
ggsave(plot = sccomp_lumb_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_lumb_all.png"), width = 6, height = 6)
```

## Imm - basal
```{r}
sccomp_basal <- readRDS(file.path(PATH, "results/sccomp/imm/pam_basal.rds"))
sccomp_basal_df <- sccomp_basal %>% sccomp_prep_data(., param = "pam_basalTRUE")
sccomp_basal_order <- sccomp_basal_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_basal_df$cluster_annot_sub <- str_replace(sccomp_basal_df$cluster_annot_sub, "_", " ")
```

```{r}
sccomp_basal_plot <- sccomp_plot_data(sccomp_basal_df)
ggsave(plot = sccomp_basal_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_basal_all.png"), width = 6, height = 6)
```

## Imm - her2
```{r}
sccomp_her2 <- readRDS(file.path(PATH, "results/sccomp/imm/pam_her2.rds"))
sccomp_her2_df <- sccomp_her2 %>% sccomp_prep_data(., param = "pam_her2TRUE")
sccomp_her2_order <- sccomp_her2_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_her2_df$cluster_annot_sub <- str_replace(sccomp_her2_df$cluster_annot_sub, "_", " ")
```

```{r}
sccomp_her2_plot <- sccomp_plot_data(sccomp_her2_df)
ggsave(plot = sccomp_her2_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_pamher2_all.png"), width = 6, height = 6)
```

## Imm - norm
```{r}
sccomp_norm <- readRDS(file.path(PATH, "results/sccomp/imm/pam_norm.rds"))
sccomp_norm_df <- sccomp_norm %>% sccomp_prep_data(., param = "pam_normTRUE")
sccomp_norm_order <- sccomp_norm_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_norm_df
```

```{r}
sccomp_norm_plot <- sccomp_plot_data(sccomp_norm_df)
ggsave(plot = sccomp_norm_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_norm_all.png"), width = 6, height = 6)
```

## Imm - sub tnbc
```{r}
sccomp_tnbc <- readRDS(file.path(PATH, "results/sccomp/imm/sub_tnbc.rds"))
sccomp_tnbc_df <- sccomp_tnbc %>% sccomp_prep_data(., annot_col = "cluster_annot_sub", param = "sub_tnbcTRUE")
sccomp_tnbc_order <- sccomp_tnbc_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_tnbc_df$cluster_annot_sub <- str_replace_all(sccomp_tnbc_df$cluster_annot_sub, "_", " ") 
```

```{r}
sccomp_tnbc_plot <- sccomp_plot_data(sccomp_tnbc_df, annot_col = "cluster_annot_sub")
ggsave(plot = sccomp_tnbc_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_tnbc_all.png"), width = 6, height = 7)
```

## Imm - sub her2
```{r}
sccomp_her2 <- readRDS(file.path(PATH, "results/sccomp/imm/sub_her2.rds"))
sccomp_her2_df <- sccomp_her2 %>% sccomp_prep_data(., annot_col = "cluster_annot_sub",param = "sub_her2TRUE")
sccomp_her2_order <- sccomp_her2_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_her2_df$cluster_annot_sub <- str_replace_all(sccomp_her2_df$cluster_annot_sub, "_", " ") 
sccomp_her2_df$c_FDR[sccomp_her2_df$c_FDR == 0] <- min(sccomp_her2_df$c_FDR[sccomp_her2_df$c_FDR > 0])
```

```{r}
sccomp_her2_plot <- sccomp_plot_data(sccomp_her2_df,annot_col = "cluster_annot_sub")
ggsave(plot = sccomp_her2_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_her2_all.png"), width = 6, height = 7)
```

## Imm - suber
```{r}
sccomp_er <- readRDS(file.path(PATH, "results/sccomp/imm/sub_er.rds"))
sccomp_er_df <- sccomp_er %>% sccomp_prep_data(., annot_col = "cluster_annot_sub",param = "sub_erTRUE")
sccomp_er_order <- sccomp_er_df %>% arrange(desc(y)) %>% pull(cluster_annot_sub)
sccomp_er_df$cluster_annot_sub <- str_replace_all(sccomp_er_df$cluster_annot_sub, "_", " ") 
```

```{r}
sccomp_er_plot <- sccomp_plot_data(sccomp_er_df,annot_col = "cluster_annot_sub")
ggsave(plot = sccomp_er_plot, filename = file.path(PATH, "results/final_figures/sccomp_imm_er_all.png"), width = 6, height = 7)
```

## Strom - sub tnbc
```{r}
sccomp_tnbc <- readRDS(file.path(PATH, "results/sccomp/strom/sub_tnbc.rds"))
sccomp_tnbc_df <- sccomp_tnbc %>% sccomp_prep_data(., param = "sub_tnbcTRUE")
sccomp_tnbc_order <- sccomp_tnbc_df %>% arrange(desc(y)) %>% pull(cluster_annot)
sccomp_tnbc_df$cluster_annot <- str_replace(sccomp_tnbc_df$cluster_annot, "_", " ") 
```

```{r}
sccomp_tnbc_plot <- sccomp_plot_data(sccomp_tnbc_df)
ggsave(plot = sccomp_tnbc_plot, filename = file.path(PATH, "results/final_figures/sccomp_strom_tnbc_all.png"), width = 6, height = 6)
```

## Strom - sub her2
```{r}
sccomp_her2 <- readRDS(file.path(PATH, "results/sccomp/strom/sub_her2.rds"))
sccomp_her2_df <- sccomp_her2 %>% sccomp_prep_data(., param = "sub_her2TRUE")
sccomp_her2_order <- sccomp_her2_df %>% arrange(desc(y)) %>% pull(cluster_annot)
sccomp_her2_df$cluster_annot <- str_replace(sccomp_her2_df$cluster_annot, "_", " ") 
```

```{r}
sccomp_her2_plot <- sccomp_plot_data(sccomp_her2_df)
ggsave(plot = sccomp_her2_plot, filename = file.path(PATH, "results/final_figures/sccomp_strom_her2_all.png"), width = 6, height = 6)
```

## Strom - suber
```{r}
sccomp_er <- readRDS(file.path(PATH, "results/sccomp/strom/sub_er.rds"))
sccomp_er_df <- sccomp_er %>% sccomp_prep_data(., param = "sub_erTRUE")
sccomp_er_order <- sccomp_er_df %>% arrange(desc(y)) %>% pull(cluster_annot)
sccomp_er_df$cluster_annot <- str_replace(sccomp_er_df$cluster_annot, "_", " ")
```

```{r}
sccomp_er_plot <- sccomp_plot_data(sccomp_er_df)
ggsave(plot = sccomp_er_plot, filename = file.path(PATH, "results/final_figures/sccomp_strom_er_all.png"), width = 6, height = 6)
```

## epi - sub tnbc
```{r}
sccomp_tnbc <- readRDS(file.path(PATH, "results/sccomp/epi/sub_tnbc.rds"))
sccomp_tnbc_df <- sccomp_tnbc %>% sccomp_prep_data(., param = "sub_tnbcTRUE", annot_col ="RNA_snn_res.0.1")
sccomp_tnbc_df$c_FDR[sccomp_tnbc_df$c_FDR == 0] <- min(sccomp_tnbc_df$c_FDR[sccomp_tnbc_df$c_FDR > 0])
sccomp_tnbc_order <- sccomp_tnbc_df %>% arrange(desc(y)) %>% pull(`RNA_snn_res.0.1`)
```

```{r}
sccomp_tnbc_plot <- sccomp_plot_data(sccomp_tnbc_df, annot_col ="RNA_snn_res.0.1")
ggsave(plot = sccomp_tnbc_plot, filename = file.path(PATH, "results/final_figures/sccomp_epi_tnbc_all.png"), width = 6, height = 6)
```

## epi - sub her2
```{r}
sccomp_her2 <- readRDS(file.path(PATH, "results/sccomp/epi/sub_her2.rds"))
sccomp_her2_df <- sccomp_her2 %>% sccomp_prep_data(., param = "sub_her2TRUE", annot_col ="RNA_snn_res.0.1")
sccomp_her2_order <- sccomp_her2_df %>% arrange(desc(y)) %>% pull(`RNA_snn_res.0.1`)
```

```{r}
sccomp_her2_plot <- sccomp_plot_data(sccomp_her2_df, annot_col ="RNA_snn_res.0.1")
ggsave(plot = sccomp_her2_plot, filename = file.path(PATH, "results/final_figures/sccomp_epi_her2_all.png"), width = 6, height = 6)
```

## epi - suber
```{r}
sccomp_er <- readRDS(file.path(PATH, "results/sccomp/epi/sub_er.rds"))
sccomp_er_df <- sccomp_er %>% sccomp_prep_data(., param = "sub_erTRUE", annot_col ="RNA_snn_res.0.1")
sccomp_er_order <- sccomp_er_df %>% arrange(desc(y)) %>% pull(`RNA_snn_res.0.1`)
```

```{r}
sccomp_er_plot <- sccomp_plot_data(sccomp_er_df, annot_col ="RNA_snn_res.0.1")
ggsave(plot = sccomp_er_plot, filename = file.path(PATH, "results/final_figures/sccomp_epi_er_all.png"), width = 6, height = 6)
```

# Figure 7 CTDS
```{r}
imm_subset <- readRDS(file.path(PATH, "data/sc/imm_rpca_sub_clean.rds"))
strom_subset <- readRDS(file.path(PATH, "data/sc/strom_rpca_subset.rds"))
epi_subset <- readRDS(file.path(PATH, "data/sc/epi_rpca_subset.rds"))

pam50 <- read.csv(file.path(PATH, "data/metadata/pam50.csv"), row.names = NULL)[,2:3]
pam50$pam50 <- str_replace(pam50$pam50, "Normal", "Normal-like")

imm_subset$donor <- str_replace_all(imm_subset$donor, pattern = "-", replacement = "_")
strom_subset$donor <- str_replace_all(strom_subset$donor, pattern = "-", replacement = "_")
epi_subset$donor <- str_replace_all(epi_subset$donor, pattern = "-", replacement = "_")

imm_subset$age_bin <- with(imm_subset@meta.data, if_else(age < median(imm_subset$age, na.rm = TRUE), "Young", "Old"))
strom_subset$age_bin <- with(strom_subset@meta.data, if_else(age < median(strom_subset$age, na.rm = TRUE), "Young", "Old"))
epi_subset$age_bin <- with(epi_subset@meta.data, if_else(age < median(epi_subset$age, na.rm = TRUE), "Young", "Old"))

imm_metadata <- dplyr::left_join(imm_subset@meta.data,
                                 pam50,
                                 by = "donor")
strom_metadata <- dplyr::left_join(strom_subset@meta.data,
                                   pam50,
                                   by = "donor")
epi_metadata <- dplyr::left_join(epi_subset@meta.data,
                                   pam50,
                                   by = "donor")
imm_ctds <- CTDS.score(imm_subset, 
                       sample = 'donor',
                       cell.type = 'cluster_annot_sub')
imm_ctds <- dplyr::inner_join(imm_ctds, 
                              imm_metadata, 
                              by = "donor")
strom_ctds <- CTDS.score(strom_subset, 
                         sample = 'donor',
                         cell.type = 'cluster_annot')
strom_ctds <- dplyr::inner_join(strom_ctds, 
                                strom_metadata,
                                by = "donor")
epi_ctds <- CTDS.score(epi_subset, 
                         sample = 'donor',
                         cell.type = 'RNA_snn_res.0.1')
epi_ctds <- dplyr::inner_join(epi_ctds, 
                                epi_metadata,
                                by = "donor")
imm_ctds$compartment <- "Immune"
strom_ctds$compartment <- "Stromal"
epi_ctds$compartment <- "Epi"
imm_strom_epi_ctds <- rbind(imm_ctds %>% dplyr::select("donor", "statistic", "subtype_new", "pam50", "grade", "age_bin", "batch", "compartment"), 
                        strom_ctds %>% dplyr::select("donor", "statistic", "subtype_new", "pam50", "grade", "age_bin", "batch", "compartment"),
                        epi_ctds %>% dplyr::select("donor", "statistic", "subtype_new", "pam50", "grade", "age_bin", "batch", "compartment"))
```

## Barcharts

### Subtype
```{r}
ditto_pal <- DiscretePalette_scCustomize(num_colors = 3, palette="ditto_seq")
imm_strom_epi_ctds %>% 
  dplyr::filter(subtype_new != "Unassigned") %>%
  ggplot(aes(x = compartment, y = statistic, fill = subtype_new)) +
  scale_fill_manual(values = ditto_pal) +
  geom_boxplot() + 
  labs(x = "Compartment", y = "CTDS", fill = "Subtype") +
  theme_minimal() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
ggsave(filename = file.path(PATH, "results/final_figures/ctds_subtype_box.png"), width = 8, height = 6)
```

### Pam50
```{r}
ditto_pal <- DiscretePalette_scCustomize(num_colors = 5, palette="ditto_seq")
imm_strom_epi_ctds$pam50 <- factor(imm_strom_epi_ctds$pam50, levels = c("LumA", "LumB", "Her2", "Basal", "Normal-like"))
imm_strom_epi_ctds %>% 
  ggplot(aes(x = compartment, y = statistic, fill = pam50)) +
  scale_fill_manual(values = ditto_pal) +
  geom_boxplot() + 
  labs(x = "Compartment", y = "CTDS",  fill = "Pam50") +
  theme_minimal() + 
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
ggsave(filename = file.path(PATH, "results/final_figures/ctds_pam50_box.png"), width = 8, height = 6)
```

### Age
```{r}
ditto_pal <- DiscretePalette_scCustomize(num_colors = 2, palette="ditto_seq")
imm_strom_epi_ctds$age_bin <- factor(imm_strom_epi_ctds$age_bin, levels = c("Young", "Old"))
imm_strom_epi_ctds %>% 
  dplyr::select(compartment, statistic, age_bin) %>% 
  tidyr::drop_na() %>%
  ggplot(aes(x = compartment, y = statistic, fill = age_bin)) +
  scale_fill_manual(values = ditto_pal) +
  geom_boxplot() + 
  labs(x = "Compartment", y = "CTDS", fill = "Age Group") +
  theme_minimal() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
ggsave(filename = file.path(PATH, "results/final_figures/ctds_age_box.png"), width = 8, height = 6)
```

### Grade
```{r}
ditto_pal <- DiscretePalette_scCustomize(num_colors = 3, palette="ditto_seq")
imm_strom_epi_ctds %>% 
  dplyr::select(compartment, statistic, grade) %>%
  tidyr::drop_na() %>%
  ggplot(aes(x = compartment, y = statistic, fill = factor(grade))) +
  scale_fill_manual(values = ditto_pal) +
  geom_boxplot() + 
  labs(x = "Compartment", y = "CTDS", fill = "Grade") +
  theme_minimal() +
  theme(text = element_text(size = 20),
        axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
ggsave(filename = file.path(PATH, "results/final_figures/ctds_grade_box.png"), width = 8, height = 6)
```

## Regressions
```{r}
imm_ctds <- imm_ctds[imm_ctds$subtype_new != "Unassigned",]
imm_ctds$pam50 <- relevel(factor(imm_ctds$pam50),ref = "Normal-like")
imm_ctds$subtype_new <- relevel(factor(imm_ctds$subtype_new),ref = "ER+")
imm_ctds_pam50_lm <- lmerTest::lmer(data = imm_ctds, formula = statistic ~ pam50 + (1|batch))
imm_ctds_subtype_lm <- lmerTest::lmer(data = imm_ctds, formula = statistic ~ subtype_new + (1|batch))
imm_ctds_grade_lm <- lmerTest::lmer(data = imm_ctds, formula = statistic ~ grade + (1|batch))
imm_ctds_age_lm <- lmerTest::lmer(data = imm_ctds, formula = statistic ~ age + (1|batch))

strom_ctds <- strom_ctds[strom_ctds$subtype_new != "Unassigned",]
strom_ctds$pam50 <- relevel(factor(strom_ctds$pam50),ref = "Normal-like")
strom_ctds$subtype_new <- relevel(factor(strom_ctds$subtype_new),ref = "ER+")
strom_ctds_pam50_lm <- lmerTest::lmer(data = strom_ctds, formula = statistic ~ pam50 + (1|batch))
strom_ctds_subtype_lm <- lmerTest::lmer(data = strom_ctds, formula = statistic ~ subtype_new + (1|batch))
strom_ctds_grade_lm <- lmerTest::lmer(data = strom_ctds, formula = statistic ~ grade + (1|batch))
strom_ctds_age_lm <- lmerTest::lmer(data = strom_ctds, formula = statistic ~ age + (1|batch))
```

### Age
```{r}
ditto_pal <- DiscretePalette_scCustomize(num_colors = 5, palette="ditto_seq")
rbind(summary(imm_ctds_age_lm)$coef[2,], 
      summary(strom_ctds_age_lm)$coef[2,]) %>%
  as.data.frame %>%
  dplyr::mutate(compartment = c("Immune", "Stromal")) %>%
  ggplot(aes(x = compartment, y = Estimate, fill = compartment)) +
    geom_bar(stat = "identity", position ="dodge") +
    geom_errorbar(aes(ymin = Estimate - `Std. Error`, ymax = Estimate + `Std. Error`), position = position_dodge(width = 0.9), width = 0.5) +
    labs(x = "Compartment", y = "Estimate", title = "Age") +
    scale_fill_manual(values = ditto_pal) +
    theme(text = element_text(size = 20),
          legend.position = "none",
          axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
```

### Subtype
```{r}
rbind(summary(imm_ctds_subtype_lm)$coef[2:3,], 
      summary(strom_ctds_subtype_lm)$coef[2:3,]) %>%
  as.data.frame %>%
  dplyr::mutate(compartment = rep(c("Immune", "Stromal"), each = 2)) %>%
  dplyr::mutate(subtype_new = rep(c("HER2", "TNBC"), 2)) %>%
  ggplot(aes(x = compartment, y = Estimate, fill = subtype_new)) +
    geom_bar(stat = "identity", position ="dodge") +
    geom_errorbar(aes(ymin = Estimate - `Std. Error`, ymax = Estimate + `Std. Error`), position = position_dodge(width = 0.9), width = 0.5) +
    labs(x = "Compartment", y = "Estimate", title = "Subtype (relative to ER+)", fill = "Subtype") +
    scale_fill_manual(values = ditto_pal) +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
```

### Pam50
```{r}
rbind(summary(imm_ctds_pam50_lm)$coef[2:5,], 
      summary(strom_ctds_pam50_lm)$coef[2:5,]) %>%
  as.data.frame %>%
  dplyr::mutate(compartment = rep(c("Immune", "Stromal"), each = 4)) %>%
  dplyr::mutate(pam50 = rep(c("Basal", "Her2", "LumA", "LumB"), 2)) %>%
  ggplot(aes(x = compartment, y = Estimate, fill = pam50)) +
    geom_bar(stat = "identity", position ="dodge") +
    geom_errorbar(aes(ymin = Estimate - `Std. Error`, ymax = Estimate + `Std. Error`), position = position_dodge(width = 0.9), width = 0.5) +
    labs(x = "Compartment", y = "Estimate", title = "pam50 (relative to normal-like)", fill = "Pam50") +
    scale_fill_manual(values = ditto_pal) +
    theme(text = element_text(size = 20),
          axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
```

### Grade
```{r}
rbind(summary(imm_ctds_grade_lm)$coef[2,], 
      summary(strom_ctds_grade_lm)$coef[2,]) %>%
  as.data.frame %>%
  dplyr::mutate(compartment = c("Immune", "Stromal")) %>%
  ggplot(aes(x = compartment, y = Estimate, fill = compartment)) +
    geom_bar(stat = "identity", position ="dodge") +
    geom_errorbar(aes(ymin = Estimate - `Std. Error`, ymax = Estimate + `Std. Error`), position = position_dodge(width = 0.9), width = 0.5) +
    labs(x = "Compartment", y = "Estimate", title = "Grade") +
    scale_fill_manual(values = ditto_pal) +
    theme(text = element_text(size = 20),
          legend.position = "none",
          axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1))
```

# Figure 8 Survival

## Epi Adj. Survival
```{r}
library(brcasurv)
# devtools::load_all("/restricted/projectnb/brcameta/personal/andrewdr/brcasurv")
# K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Epi 2025_02_14_11_49_43/K2results.rds"))
# K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_epi_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_epi_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_epi_gsva.rds"))
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
K2visNetwork(K2summary) %>% visHierarchicalLayout()
```

```{r}
for (node_name in c("D_1_up", "G_1_up", "N_2_up", "L_2_up", "J_2_up", "H_2_up", "I_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```


### Combined
```{r}
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")

new_branch_cols <- rep("#000000",  length(all_nodes_labels))

green_idx <- c(which(all_nodes_labels %in% c("A","B","E")) + 1,
               which(all_nodes_labels %in% c("E")),
               which(all_nodes_labels %in% c("0","14","8","16","5","6","17")) - 1,
               which(all_nodes_labels %in% c("0","14","8","16","5","6","17"))
             )
new_branch_cols[green_idx] <- "darkgreen"

new_branch_lwd <- rep(1, length(all_nodes_labels))
new_branch_lwd[green_idx] <- 3
two_data_evidence <- c(which(all_nodes_labels %in% c("8")) - 1,
                       which(all_nodes_labels %in% c("8")))
new_branch_lwd[two_data_evidence] <- 5

k2_epi_dend <- K2dendrogram %>% set("branches_col", new_branch_cols) %>% set("labels_cex", 1) %>% set("branches_lwd", new_branch_lwd)
png(file.path(PATH, "results/final_figures/survival_epi_combined.png"), width = 800, height = 600, res=180) # Width and height in pixels
k2_epi_dend %>% plot
dev.off()
```


## Imm Adj. Survival
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Imm 2025_09_03_20_15_46/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_imm_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_imm_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_imm_gsva.rds"))
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
for (node_name in c("AA_1_up", "U_2_up", "Q_2_up", "D_2_up",
                    "DD_1_up", "Y_2_up", "E_2_up", "O_2_up", "K_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

### Combined
```{r}
labels(K2dendrogram) <- str_replace_all(labels(K2dendrogram), "_", " ")
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")

new_branch_cols <- rep("#000000",  length(all_nodes_labels))

red_idx <- c(which(all_nodes_labels %in% c("C")) + 1,
             which(all_nodes_labels %in% c("Mac RTM MT")) - 1,
             which(all_nodes_labels %in% c("Mac RTM MT"))
)

green_idx <- c(which(all_nodes_labels %in% c("A","B","D","E","G","H","I","S","T","Z")) + 1,
               which(all_nodes_labels %in% c("C","S","U","X")),
               which(all_nodes_labels %in% c("B ACB", "CD4 Tem", "Plasma IgG", "Mast", "Mac RTM LA", "cDC1","B Naive","CD8 Tex")) - 1,
               which(all_nodes_labels %in% c("B ACB", "CD4 Tem", "Plasma IgG", "Mast", "Mac RTM LA", "cDC1","B Naive","CD8 Tex"))
             )
new_branch_cols[green_idx] <- "darkgreen"
new_branch_cols[red_idx] <- "darkred"

new_branch_lwd <- rep(1, length(all_nodes_labels))
new_branch_lwd[green_idx] <- 3
new_branch_lwd[red_idx] <- 3
two_data_evidence <- c(which(all_nodes_labels %in% c("B")) + 1,
                       which(all_nodes_labels %in% c("Mast")) - 1,
                       which(all_nodes_labels %in% c("Mast")))
new_branch_lwd[two_data_evidence] <- 5

k2_imm_dend <- K2dendrogram %>% set("branches_col", new_branch_cols) %>% set("labels_cex", 0.6) %>% set("branches_lwd", new_branch_lwd)
png(file.path(PATH, "results/final_figures/survival_imm_combined.png"), width = 800, height = 600, res=180) # Width and height in pixels
k2_imm_dend %>% plot
dev.off()
```

```{r}
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")

new_branch_cols <- rep("#000000",  length(all_nodes_labels))

k2_epi_dend <- K2dendrogram %>% set("branches_col", new_branch_cols) %>% set("labels_cex", 1) %>% set("branches_lwd", 2)
png(file.path(PATH, "results/final_figures/survival_imm_blank.png"), width = 800, height = 600, res=180) # Width and height in pixels
k2_epi_dend %>% plot
dev.off()
```

## Strom Adj. Survival
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Strom 2025_02_14_10_20_28/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_strom_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_strom_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_strom_gsva.rds"))
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
for (node_name in c("L_1_up", "H_2_up", "I_1_up", "I_2_up","E_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

### Combined
```{r}
all_nodes_labels <- K2dendrogram %>% get_nodes_attr("label")

new_branch_cols <- rep("#000000",  length(all_nodes_labels))

red_idx <- c(which(all_nodes_labels %in% c("A", "B","C")) + 1,
             which(all_nodes_labels %in% c("6","0","8","4","1")) - 1,
             which(all_nodes_labels %in% c("6","0","8","4","1"))
)

new_branch_cols[red_idx] <- "darkred"

new_branch_lwd <- rep(1, length(all_nodes_labels))
new_branch_lwd[red_idx] <- 3

labels(K2dendrogram) <- c("Endo Lymph.", "Endo Capil.", "Endo Ven.", "Endo Arter.", "Endo. Imm.", 
                      "CAFs (P16+)", "CAFs (DPT+)", "CAFs (LAMP5)", "CAFs (COL11A1+)", "CAFs (CA12+)",
                      "Prolif Stromal", "PCs (ECM)", "Myofibroblast", "VSMC")
k2_strom_dend <- K2dendrogram %>% set("branches_col", new_branch_cols) %>% set("labels_cex", 0.7) %>% set("branches_lwd", new_branch_lwd)
png(file.path(PATH, "results/final_figures/survival_strom_combined.png"), width = 800, height = 600, res=180) # Width and height in pixels
k2_strom_dend %>% plot
dev.off()
```

# Survival - LumB

## Epi Adj. Survival
```{r}
library(brcasurv)
# devtools::load_all("/restricted/projectnb/brcameta/personal/andrewdr/brcasurv")
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Epi 2025_02_14_11_49_43/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_epi_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_epi_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_epi_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subtype = "LumB",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "LumB",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "LumB",
                               subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```

```{r}
for (node_name in c("G_2_up", "K_2_up", "O_1_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

## Imm Adj. Survival

```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Imm 2025_09_03_20_15_46/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_imm_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_imm_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_imm_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subset_subtype = TRUE,
                              subtype = "LumB",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva,
                                  subset_subtype = TRUE,
                              subtype = "LumB",
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva,
                               subset_subtype = TRUE,
                              subtype = "LumB",
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
for (node_name in c("E_2_up", "G_2_up",
                    "I_2_up", "T_2_up", "Q_2_up", 
                    "X_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```
```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```

## Strom Adj. Survival
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Strom 2025_02_14_10_20_28/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_strom_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_strom_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_strom_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              subtype = "LumB",
                              subset_subtype = TRUE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "LumB",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "LumB",
                              subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
for (node_name in c("E_2_up", "F_1_up", "K_1_up", "L_1_up", "L_2_up", "M_1_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

# Survival - Her2

## Epi Adj. Survival
```{r}
library(brcasurv)
library(K2Taxonomer)
# devtools::load_all("/restricted/projectnb/brcameta/personal/andrewdr/brcasurv")
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Epi 2025_02_14_11_49_43/K2results.rds"))
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_epi_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_epi_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_epi_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subtype = "Her2",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "Her2",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "Her2",
                               subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```

```{r}
for (node_name in c("G_2_up", "K_2_up", "O_1_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```


## Imm Adj. Survival

```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Imm 2025_09_03_20_15_46/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_imm_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_imm_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_imm_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subset_subtype = TRUE,
                              subtype = "Her2",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva,
                                  subset_subtype = TRUE,
                              subtype = "Her2",
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva,
                               subset_subtype = TRUE,
                              subtype = "Her2",
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```
```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```

```{r}
for (node_name in c("G_2_up", "V_1_up",
"AA_1_up","DD_1_up", "H_2_up",
"Q_2_up", "U_2_up", "V_2_up",
"X_1_up", "X_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

## Strom Adj. Survival
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Strom 2025_02_14_10_20_28/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_strom_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_strom_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_strom_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              subtype = "Her2",
                              subset_subtype = TRUE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "Her2",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "Her2",
                              subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
for (node_name in c("I_1_up", "L_1_up", "L_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```


```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

# Survival - Basal

## Epi Adj. Survival
```{r}
library(brcasurv)
# devtools::load_all("/restricted/projectnb/brcameta/personal/andrewdr/brcasurv")
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Epi 2025_02_14_11_49_43/K2results.rds"))
# K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_epi_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_epi_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_epi_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```


```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subtype = "Basal",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "Basal",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "Basal",
                               subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```

```{r}
for (node_name in c("D_1_up", "G_1_up", "N_2_up", "L_2_up", "J_2_up", "H_2_up", "I_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```


## Imm Adj. Survival

```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Imm 2025_09_03_20_15_46/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_imm_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_imm_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_imm_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subset_subtype = TRUE,
                              subtype = "Basal",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva,
                                  subset_subtype = TRUE,
                              subtype = "Basal",
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva,
                               subset_subtype = TRUE,
                              subtype = "Basal",
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
K2visNetwork(K2summary) %>% visNetwork::visHierarchicalLayout()
```

```{r}
for (node_name in c("CC_1_up", "J_1_up","V_2_up", "X_1_up", "X_2_")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

## Strom Adj. Survival
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Strom 2025_02_14_10_20_28/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_strom_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_strom_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_strom_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              subtype = "LumA",
                              subset_subtype = TRUE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "LumA",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "LumA",
                              subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
for (node_name in c("L_1_up", "H_2_up", "I_1_up", "I_2_up","E_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

# Survival - LumA

## Epi Adj. Survival
```{r}
library(brcasurv)
# devtools::load_all("/restricted/projectnb/brcameta/personal/andrewdr/brcasurv")
# K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Epi 2025_02_14_11_49_43/K2results.rds"))
# K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_epi_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_epi_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_epi_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```


```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subtype = "LumA",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "LumA",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "LumA",
                               subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
K2visNetwork(K2summary) %>% visHierarchicalLayout()
```

```{r}
for (node_name in c("D_1_up", "G_1_up", "N_2_up", "L_2_up", "J_2_up", "H_2_up", "I_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```


## Imm Adj. Survival

```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Imm 2025_09_03_20_15_46/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_imm_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_imm_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_imm_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              brca_data = "TCGA",
                              subset_subtype = TRUE,
                              subtype = "LumA",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva,
                                  subset_subtype = TRUE,
                              subtype = "LumA",
                              brca_data = "METABRIC",
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE,
                              ph_filter = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva,
                               subset_subtype = TRUE,
                              subtype = "LumA",
                               brca_data = "SCANB",
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE,
                               ph_filter = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

```{r}
for (node_name in c("AA_1_up", "AA_2_up", "CC_2_up",
                    "D_2_up", "DD_1_up", "K_2_up", "L_2_up", 
                    "T_2_up", "U_2_up", "V_1_up", "W_1_up", "Y_1_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

## Strom Adj. Survival
```{r}
K2summary <- readRDS(file.path(PATH, "results/k2/K2Taxonomer_Strom 2025_02_14_10_20_28/K2results.rds"))
K2dendrogram <- K2dendro(K2summary)
```

```{r}
tcga_gsva <- readRDS(file.path(PATH, "results/gsva/tcga_strom_gsva.rds"))
metabric_gsva <- readRDS(file.path(PATH, "results/gsva/metabric_strom_gsva.rds"))
scanb_gsva <- readRDS(file.path(PATH, "results/gsva/scanb_strom_gsva.rds"))
```

```{r}
tcga_gsva <- as(tcga_gsva, "SummarizedExperiment")
metabric_gsva <- as(metabric_gsva, "SummarizedExperiment")
scanb_gsva <- as(scanb_gsva, "SummarizedExperiment")
names(tcga_gsva@assays) <- "es"
names(metabric_gsva@assays) <- "es"
names(scanb_gsva@assays) <- "es"
```

```{r}
## TCGA
tcga_cox_data <- gsva_cox_fit(tcga_gsva, 
                              five_year = FALSE,
                              subtype = "LumA",
                              subset_subtype = TRUE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
tcga_cox_fits <- p_adjust_list(tcga_cox_data$cox_fits)
tcga_ph_tests <- tcga_cox_data$ph_tests

## METABRIC
metabric_cox_data <- gsva_cox_fit(metabric_gsva, 
                              brca_data = "METABRIC",
                              subtype = "LumA",
                              subset_subtype = TRUE,
                              five_year = FALSE,
                              adjust_age = TRUE,
                              adjust_prolif = TRUE,
                              adjust_inflam = TRUE)
metabric_cox_fits <- p_adjust_list(metabric_cox_data$cox_fits)
metabric_ph_tests <- metabric_cox_data$ph_tests

## SCANB
scanb_cox_data <- gsva_cox_fit(scanb_gsva, 
                               brca_data = "SCANB",
                               subtype = "LumA",
                              subset_subtype = TRUE,
                               five_year = FALSE,
                               adjust_age = TRUE,
                               adjust_prolif = TRUE,
                               adjust_inflam = TRUE)
scanb_cox_fits <- p_adjust_list(scanb_cox_data$cox_fits)
scanb_ph_tests <- scanb_cox_data$ph_tests
```


```{r}
tcga_top_hazard <- lapply(tcga_cox_fits, filter_fit)
tcga_bottom_hazard <- lapply(tcga_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

metabric_top_hazard <- lapply(metabric_cox_fits, filter_fit)
metabric_bottom_hazard <- lapply(metabric_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)

scanb_top_hazard <- lapply(scanb_cox_fits, filter_fit)
scanb_bottom_hazard <- lapply(scanb_cox_fits, filter_fit, pos_only = FALSE, neg_only = TRUE)
```

```{r}
tcga_top_nodes <- tcga_top_hazard[which(!(lapply(tcga_top_hazard, is.null) %>% unlist))]
tcga_bottom_nodes <- tcga_bottom_hazard[which(!(lapply(tcga_bottom_hazard, is.null) %>% unlist))]
metabric_top_nodes <- metabric_top_hazard[which(!(lapply(metabric_top_hazard, is.null) %>% unlist))]
metabric_bottom_nodes <- metabric_bottom_hazard[which(!(lapply(metabric_bottom_hazard, is.null) %>% unlist))]
scanb_top_nodes <- scanb_top_hazard[which(!(lapply(scanb_top_hazard, is.null) %>% unlist))]
scanb_bottom_nodes <- scanb_bottom_hazard[which(!(lapply(scanb_bottom_hazard, is.null) %>% unlist))]
```

```{r}
for (node_name in c("L_1_up", "H_2_up", "I_1_up", "I_2_up","E_2_up")) {
  print(node_name)
  print(tcga_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(metabric_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
  print(scanb_cox_fits[[node_name]][node_name, c("exp(coef)", "p.adj")])
}
```

```{r}
table(c(names(tcga_top_nodes), names(metabric_top_nodes), names(scanb_top_nodes)))
```

```{r}
table(c(names(tcga_bottom_nodes), names(metabric_bottom_nodes), names(scanb_bottom_nodes)))
```

